### 2020-10-19 reports/interactive-rbans.Rmd
Adds interactive rbans report

---
title: "Interactive report of the RBANS results"
author: "Lukáš 'hejtmy' Hejtmánek"
date: "25/03/2020"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: rows
---
```{r setup, message=FALSE, warning=FALSE, results='hide', echo=FALSE}
library(plotly)
library(crosstalk)
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
opts_knit$set(root.dir = "../")

source("../functions/cdz-loading-pilot.R")
source("../functions/cdz-analysis.R")
source("../functions/cdz-helpers.R")
source("../functions/cdz-getters.R")
source("../functions/cdz-preprocess.R")
```

```{r loading}
df_ids <- get_sheet_ids()
df_demographics <- get_sheet_demographics()
df_sessions <- get_sheet_sessions()
df_rbans <- get_sheet_rbans()
```

```{r preprocessing}
df_rbans <- add_session_to_rbans(df_rbans, df_demographics)
df_rbans_long <- df_rbans %>%
    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
                 names_to = "subtest", values_to = "score")
df_rbans_long <- df_rbans_long %>%
  group_by(trenink, first_training, subtest) %>%
  summarise(group_avg = mean(score, na.rm = TRUE)) %>%
  ungroup() %>%
  right_join(df_rbans_long, by = c("trenink", "first_training", "subtest"))

df_rbans_long <- df_rbans_long %>%
  arrange(rbansid, session)
```

```{r}
shared_rbans <- SharedData$new(df_rbans_long)
```

Row {data-height=200}
---------------------------
### Visualisation of RBANS in different sessions
```{r}
selection_widget <- bscols(
  widths = 6,
  filter_select("subtest", "Subtest", shared_rbans, ~subtest, multiple = FALSE),
  filter_select("first_training", "Group", shared_rbans, ~first_training, multiple = FALSE)
)
selection_widget
```

Row {data-height=600}
---------------------------

### Visualisation of RBANS in different sessions

```{r}
plot_ly(shared_rbans, x = ~session, y = ~score) %>%
  add_trace(type = "box",  color = ~as.factor(session),
            hoverinfo = "y", showlegend = TRUE, boxmean = TRUE) %>%
  layout(showlegend = FALSE, autosize = TRUE, height = 500)
```

### Visualisation of RBANS in different sessions

```{r}
plot_ly(shared_rbans, x = ~session, y = ~score) %>%
  add_trace(type = "scatter", x=~session, y = ~score,
            mode = "lines+markers", split = ~rbansid) %>%
  layout(showlegend = FALSE, autosize = TRUE, height = 500)
```

```{r eval = FALSE}
df_rbans_long %>%
  filter(subtest == "iq_celek") %>%
  filter(first_training == "TP") %>%
  plot_ly(x= ~session, y = ~score) %>%
   add_trace(type = "box",  color = ~as.factor(session),
            hoverinfo = "y", showlegend = TRUE, boxmean = TRUE) %>%
  add_trace(type = "scatter", y = ~score,
            mode = "lines+markers", split = ~rbansid) %>%
  layout(showlegend=FALSE)
````

### 2020-10-19 reports/rbans-output.Rmd
Adds interactive rbans report

---
title: "Rbans-output"
author: "Lukáš 'hejtmy' Hejtmánek"
date: "15/10/2020"
output: html_document
---

```{r setup, include=FALSE}
library(brainvr.supermarket)
library(googlesheets4)
library(tidyverse)
library(knitr)
library(plotly)
knitr::opts_chunk$set(echo = FALSE)

source("../functions/cdz-loading-pilot.R")
source("../functions/cdz-analysis.R")
source("../functions/cdz-helpers.R")
source("../functions/cdz-getters.R")
source("../functions/cdz-preprocess.R")
```

```{r loading}
df_ids <- get_sheet_ids()
df_demographics <- get_sheet_demographics()
df_sessions <- get_sheet_sessions()
df_rbans <- get_sheet_rbans()
```

```{r preprocessing}
df_rbans <- add_session_to_rbans(df_rbans, df_demographics)
df_rbans_long <- df_rbans %>%
    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
                 names_to = "subtest", values_to = "score")
df_rbans_long <- df_rbans_long %>%
  group_by(trenink, first_training, subtest) %>%
  summarise(group_avg = mean(score, na.rm = TRUE)) %>%
  right_join(df_rbans_long, by = c("trenink", "first_training", "subtest"))
```
```{r}
df_ids %>%
  count(is_ok, rbans_ok, logy_ok) %>%
  kable(caption = "Overview of the state of affairs")
```

```{r}

df_rbans_long %>%
  filter(grepl("iq_", subtest)) %>%
  plot_ly(x = ~)
  ggplot(aes(subtest, score, fill = session)) + 
  geom_boxplot() +
  geom_line(aes(x = session , y = group_avg, group=subtest), size = 1.25) +
  facet_wrap(~first_training)
```

```{r}
library(lme4)
df_rbans %>%
  lmer(iq_celek ~ session + first_training + (1|rbansid), data = .) %>%
  summary()

ggplot(df_rbans, aes(as.factor(session), iq_celek, fill=trenink)) + 
  geom_boxplot() +
  geom_jitter(width = 0.2) +
  facet_wrap(~first_training)

df_rbans %>%
  filter(first_training == "TP") %>%
  glm(iq_celek ~ session ,data = .) %>%
  summary()

df_rbans %>%
  filter(first_training == "TP") %>%
  lmer(iq_celek ~ session + (1|rbansid), data = .) %>%
  summary()

df_rbans %>%
  filter(diagnosis == "schizophrenia") %>%
  ggplot(aes(session, iq_rec)) +
    geom_line(aes(color=rbansid)) +geom_point() +
    facet_wrap(~first_training)

## ----
df_rbans_baseline <- baseline_rbans(df_rbans)
df_rbans_baseline %>%
  pivot_longer(-c(rbansid, trenink, diagnosis, first_training), names_to = "subtest") %>%
  filter(grepl("iq_", subtest)) %>%
  ggplot(aes(subtest, value, fill = trenink)) +
    geom_boxplot() +
    facet_wrap(~first_training) + geom_hline(yintercept = 0)

df_ids %>%
  left_join(select(df_demographics, rbansid, first_training), by = "rbansid") %>%
  count(is_ok, first_training)

```

### 2020-10-19 functions/cdz-getters.R

@@ -1,7 +1,7 @@
 GS_RUN2_SESSION <- "1rFm8QnjGw3BQuFfMvGiLUa5hMvg3-8iTP8h5DGMZLlc"
 GS_RUN2_DEMOGRAPHICS_RBANS <- "1qMdiLYY7EIbNvoRsE5knjBB24zXT7hgJNUCmwMX7IwY"
 
-get_sheet_ids <- function(preprocess = TRUE){
+get_sheet_ids <- function(preprocess = TRUE, overwrite = FALSE){
   df_ids <- googlesheets4::range_read(GS_RUN2_DEMOGRAPHICS_RBANS, sheet = "ID")
   if(!preprocess) return(df_ids)
   colnames(df_ids) <- tolower(colnames(df_ids))
@@ -13,7 +13,7 @@ get_sheet_ids <- function(preprocess = TRUE){
   
   return(df_ids)
 }
-get_sheet_demographics <- function(preprocess = TRUE){
+get_sheet_demographics <- function(preprocess = TRUE, overwrite = FALSE){
   df_demographics <- googlesheets4::range_read(GS_RUN2_DEMOGRAPHICS_RBANS, 
                                              sheet = "demografie", 
                                              col_types = "ccccccciiiccc")
@@ -25,7 +25,7 @@ get_sheet_demographics <- function(preprocess = TRUE){
   return(df_demographics)
 }
 
-get_sheet_rbans <- function(preprocess = TRUE){
+get_sheet_rbans <- function(preprocess = TRUE, overwrite = FALSE){
   df_rbans <- googlesheets4::range_read(GS_RUN2_DEMOGRAPHICS_RBANS,
                                         sheet = "rbans")
   if(!preprocess) return(df_rbans)
@@ -40,8 +40,8 @@ get_sheet_rbans <- function(preprocess = TRUE){
   return(df_rbans) 
 }
 
-get_sheet_sessions <- function(preprocess = TRUE){
-  df_sessions <- googlesheets4::sheets_read(GS_RUN2_SESSION, col_types = "ccicc")
+get_sheet_sessions <- function(preprocess = TRUE, overwrite = FALSE){
+  df_sessions <- googlesheets4::range_read(GS_RUN2_SESSION, col_types = "ccicc")
   if(!preprocess) returnb(df_sessions)
   colnames(df_sessions) <- tolower(colnames(df_sessions))
   return(df_sessions)

### 2020-11-06 reports/interactive-rbans.Rmd
Updates rbans with new objservations

@@
 
-Row {data-height=200}
+Row {data-height=400}
 ---------------------------

### 2020-11-06 reports/rbans-output.Rmd
Updates rbans with new objservations

@@
 ```{r}
-
 df_rbans_long %>%
   filter(grepl("iq_", subtest)) %>%
-  plot_ly(x = ~)
   ggplot(aes(subtest, score, fill = session)) +
@@
 
-## ----
 df_rbans_baseline <- baseline_rbans(df_rbans)
@@
 ```
+
+```{r}
+unique(df_rbans_long$subtest)
+c("Vybavenifigury", "vybaveniseznamu", "vybavenipovidky")
+```

### 2020-11-06 functions/cdz-getters.R

@@ -16,12 +16,12 @@ get_sheet_ids <- function(preprocess = TRUE, overwrite = FALSE){
 get_sheet_demographics <- function(preprocess = TRUE, overwrite = FALSE){
   df_demographics <- googlesheets4::range_read(GS_RUN2_DEMOGRAPHICS_RBANS, 
                                              sheet = "demografie", 
-                                             col_types = "ccccccciiiccc")
+                                             col_types = "ccccccciiiccci")
   if(!preprocess) return(df_demographics)
   colnames(df_demographics) <- c("name", "note", "first_training", "rbans_date",
                                  "rbansid", "retirement", "gender", "age",
                                  "education", "ilness_duration_years", "diagnosis",
-                                 "medication", "other_notes")
+                                 "medication", "other_notes", "GAF")
   return(df_demographics)
 }
 

### 2020-11-06 reports/interactive-rbans.Rmd
Adds updated report with standardized scores

@@
   arrange(rbansid, session)
+
+df_rbans_long <- df_rbans_long %>%
+  group_by(session, subtest) %>%
+  mutate(scaled_score = (score-mean(score, na.rm = TRUE))/sd(score, na.rm = TRUE)) %>%
+  ungroup()
 ```
@@
 
-Row {data-height=400}
+Row {data-height=300}
 ---------------------------
@@
 ```{r}
-plot_ly(shared_rbans, x = ~session, y = ~score) %>%
+plot_ly(shared_rbans, x = ~session, y = ~scaled_score) %>%
   add_trace(type = "box",  color = ~as.factor(session),
@@
 ```{r}
-plot_ly(shared_rbans, x = ~session, y = ~score) %>%
-  add_trace(type = "scatter", x=~session, y = ~score,
+plot_ly(shared_rbans, x = ~session, y = ~scaled_score) %>%
+  add_trace(type = "scatter", x=~session, y = ~scaled_score,
             mode = "lines+markers", split = ~rbansid) %>%
@@
   filter(first_training == "TP") %>%
-  plot_ly(x= ~session, y = ~score) %>%
+  plot_ly(x= ~session, y = ~scaled_score) %>%
    add_trace(type = "box",  color = ~as.factor(session),
             hoverinfo = "y", showlegend = TRUE, boxmean = TRUE) %>%
-  add_trace(type = "scatter", y = ~score,
+  add_trace(type = "scatter", y = ~scaled_score,
             mode = "lines+markers", split = ~rbansid) %>%

### 2020-11-06 reports/rbans-output.Rmd
Adds updated report with standardized scores

@@
 df_rbans %>%
-  filter(diagnosis == "schizophrenia") %>%
+  filter(!is.na(first_training)) %>%
   ggplot(aes(session, iq_rec)) +
-    geom_line(aes(color=rbansid)) +geom_point() +
-    facet_wrap(~first_training)
+    geom_line(aes(color=rbansid)) + geom_point() +
+    facet_wrap(~c(first_training, diagnosis))
 

### 2021-01-10 functions/cdz-constants.R
Fixed sheet loading with the updated logs

@@ -1,2 +1,0 @@
-GS_RUN2_SESSION <- "1rFm8QnjGw3BQuFfMvGiLUa5hMvg3-8iTP8h5DGMZLlc"
-GS_RUN2_DEMOGRAPHICS_RBANS <- "1qMdiLYY7EIbNvoRsE5knjBB24zXT7hgJNUCmwMX7IwY"

### 2021-01-10 functions/cdz-getters.R

@@ -1,6 +1,3 @@
-GS_RUN2_SESSION <- "1rFm8QnjGw3BQuFfMvGiLUa5hMvg3-8iTP8h5DGMZLlc"
-GS_RUN2_DEMOGRAPHICS_RBANS <- "1qMdiLYY7EIbNvoRsE5knjBB24zXT7hgJNUCmwMX7IwY"
-
 get_sheet_ids <- function(preprocess = TRUE, overwrite = FALSE){
   df_ids <- googlesheets4::range_read(GS_RUN2_DEMOGRAPHICS_RBANS, sheet = "ID")
   if(!preprocess) return(df_ids)
@@ -13,7 +10,9 @@ get_sheet_ids <- function(preprocess = TRUE, overwrite = FALSE){
   
   return(df_ids)
 }
+
 get_sheet_demographics <- function(preprocess = TRUE, overwrite = FALSE){
+  GS_RUN2_DEMOGRAPHICS_RBANS <- "1qMdiLYY7EIbNvoRsE5knjBB24zXT7hgJNUCmwMX7IwY"
   df_demographics <- googlesheets4::range_read(GS_RUN2_DEMOGRAPHICS_RBANS, 
                                              sheet = "demografie", 
                                              col_types = "ccccccciiiccci")
@@ -41,7 +40,8 @@ get_sheet_rbans <- function(preprocess = TRUE, overwrite = FALSE){
 }
 
 get_sheet_sessions <- function(preprocess = TRUE, overwrite = FALSE){
-  df_sessions <- googlesheets4::range_read(GS_RUN2_SESSION, col_types = "ccicc")
+  GS_RUN2_SESSION <- "1rFm8QnjGw3BQuFfMvGiLUa5hMvg3-8iTP8h5DGMZLlc"
+  df_sessions <- googlesheets4::range_read(GS_RUN2_SESSION, col_types = "ccicci")
   if(!preprocess) returnb(df_sessions)
   colnames(df_sessions) <- tolower(colnames(df_sessions))
   return(df_sessions)

### 2021-01-10 functions/cdz-getters.R
Updates sheet getting with remediation vs test column

@@ -41,8 +41,9 @@ get_sheet_rbans <- function(preprocess = TRUE, overwrite = FALSE){
 
 get_sheet_sessions <- function(preprocess = TRUE, overwrite = FALSE){
   GS_RUN2_SESSION <- "1rFm8QnjGw3BQuFfMvGiLUa5hMvg3-8iTP8h5DGMZLlc"
-  df_sessions <- googlesheets4::range_read(GS_RUN2_SESSION, col_types = "ccicci")
+  df_sessions <- googlesheets4::range_read(GS_RUN2_SESSION, col_types = "cciccic")
   if(!preprocess) returnb(df_sessions)
   colnames(df_sessions) <- tolower(colnames(df_sessions))
+  df_sessions$use <- df_sessions$use == 1
   return(df_sessions)
 }

### 2021-01-10 reports/rbans-output.Rmd
Updates to data preprocessing and buffering

--- 2020-11-06 reports/rbans-output.Rmd
@@
   kable(caption = "Overview of the state of affairs")
+
+df_rbans_long %>%
+  group_by(session) %>%
+  summarise(length(unique(rbansid)))
+
+df_ids %>%
+  left_join(select(df_demographics, rbansid, first_training), by = "rbansid") %>%
+  count(is_ok, first_training)
 ```
@@
 df_rbans %>%
-  filter(diagnosis == "schizophrenia") %>%
-  ggplot(aes(session, iq_rec)) +
-    geom_line(aes(color=rbansid)) +geom_point() +
-    facet_wrap(~first_training)
+  filter(!is.na(first_training)) %>%
+  ggplot(aes(session, vybaveniseznamu)) +
+    geom_line(aes(color=rbansid)) + geom_point() +
+    facet_wrap( ~ first_training + diagnosis)
 
@@
 
-df_ids %>%
-  left_join(select(df_demographics, rbansid, first_training), by = "rbansid") %>%
-  count(is_ok, first_training)
-
 ```

### 2021-01-10 functions/cdz-loading-pilot.R

@@ -12,7 +12,7 @@ load_participants_supermarket <- function(data_dir, ids = c()){
     ids <- list.files(file.path(data_dir, "supermarket"),
                       full.names = FALSE, recursive = FALSE)
   }
-  result <- list() 
+  result <- list()
   for(id in ids){
     folder <- path_supermarket_participant(data_dir, id)
     if(!dir.exists(folder)) next
@@ -25,6 +25,7 @@ load_participants_supermarket <- function(data_dir, ids = c()){
 
 load_participant_supermarket <- function(data_dir, id){
   folder <- path_supermarket_participant(data_dir, id)
+  message("loading ", folder)
   exps <- load_supermarket_experiments(folder, language = "CZR")
   ## ThIS DOESN'T WORK FOR ALL FOR SOME REASON FFS
   # version <- exps[[1]]$data$experiment_info$Experiment$Settings$settings[17]

### 2021-01-10 scripts/buffer-online-tables.R

@@ -1,0 +1,7 @@
+df_demographics <- get_sheet_demographics()
+df_rbans <- get_sheet_rbans()
+df_ids <- get_sheet_ids()
+
+write.table(df_ids, "information.csv", sep = ";", row.names = FALSE)
+write.table(df_demographics, "demographics.csv", sep = ";", row.names = FALSE)
+write.table(df_rbans, "rbans.csv", sep = ";", row.names = FALSE)

### 2021-01-10 scripts/run2-results-output.R

@@ -1,14 +1,55 @@
 library(brainvr.supermarket)
 library(googlesheets4)
-source("functions/constants.R")
+library(tidyverse)
 source("functions/cdz-loading-pilot.R")
 source("functions/cdz-analysis.R")
+source("functions/cdz-getters.R")
 
-demographics <- googlesheets4::sheets_read(GS_RUN2_DEMOGRAPHICS)
-df_sessions <- googlesheets4::sheets_read(GS_RUN2_SESSION,col_types = "ccicc")
+df_demographics <- get_sheet_demographics()
+df_sessions <- get_sheet_sessions()
 
 UNITY_DIR <- "E:/Google Drive/NUDZ/Projects/CDZ Karvina/VR-tasks/logy/2-pilot_VR-pen-paper/"
-participatns <- unique(df_sessions$ID)
+participatns <- unique(df_sessions$id)
+
 exps <- load_participants_supermarket(UNITY_DIR, participatns)
+names(exps)
 df_results <- supermarket_results.participants(exps)
-write.table(df_results, "run2-results.csv", sep=",", row.names = FALSE)
+
+df_results <- df_results %>% 
+  separate(timestamp, sep = "-", into = c("hour", "minute", "second", "day", "month", "year"), remove = FALSE) %>% 
+  mutate(day = gsub("[0]([0-9])", "\\1", day),
+         month = gsub("0([0-9])", "\\1", month)) %>%
+  unite("date", c(day, month, year), sep = ".") %>%
+  select(-c(hour, minute, second))
+write.table(df_results, "run2-results-supermarket.csv", sep = ";", row.names = FALSE)
+df_results <- read.table("run2-results-supermarket.csv", sep = ";", header = TRUE)
+
+df_results <- df_results %>%
+  left_join(filter(df_sessions, task == "supermarket", use),
+            by = c("participant" = "id", "date" = "date")) %>%
+  filter(!is.na(session))
+
+write.table(df_results, "run2-results-supermarket-sessions.csv", 
+            sep=";", row.names = FALSE)
+
+# Missing information about session
+df_results %>%
+  filter(is.na(session)) %>%
+  select(participant, timestamp) %>%
+  distinct()
+
+View(df_results)
+
+df_results %>%
+  filter(!is.na(session)) %>%
+  group_by(participant) %>%
+  summarise(n = n(), sessions = length(unique(session)),
+            timestamps = length(unique(timestamp)))
+
+
+df_results %>%
[…]

### 2021-01-10 reports/results.Rmd
Updates supermarket results

---
title: "results"
author: "Lukáš 'hejtmy' Hejtmánek"
date: "10/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::optlibrary(tidyverse)
knitr::opts_chunk$set(echo = FALSE)

df_results <- read.table("../run2-results-supermarket-sessions.csv", sep = ";",
                           header = TRUE)s_chunk$set(echo = TRUE)

df_ids <- read.table("../information.csv", sep = ";", header = TRUE)
df_rbans <- read.table("../information.csv", sep = ";", header = TRUE)
```

### 2021-01-10 reports/supermarket-output.Rmd
Updates supermarket results

---
title: "Supermarket ouptut"
author: "Lukáš 'hejtmy' Hejtmánek"
date: "10/01/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
df_results <- read.table("../run2-results-supermarket-sessions.csv", sep = ";",
                           header = TRUE)

df_demographics <- read.table("../demographics.csv", sep = ";", header = TRUE)
df_ids <- read.table("../information.csv", header = TRUE, sep = ";")

# Combine with demographics
df_join <- df_demographics %>%
  left_join(df_ids, by = "rbansid") %>%
  select(rbansid, vrid) %>% 
  filter(!is.na(rbansid) & !is.na(vrid))

df_results <- df_results %>%
  left_join(df_join, by = c("participant" = "vrid"))
```

```{r}
df_results <- df_results %>%
  mutate(total_picked_items = n_correct_items + n_extra_items,
         correct_ratio = n_correct_items/n_items,
         extra_ratio = n_extra_items/n_items) %>%
  group_by(participant, session) %>%
  mutate(n_trials = n()) %>%
  ungroup()

df_results <- filter(df_results, session <= 12)

df_results_remediation <- filter(df_results, type == "remediation")
df_results_test <- filter(df_results, type == "test")
```

```{r}
df_results_remediation %>%
  group_by(participant, session) %>%
  summarise(correct_ratio = mean(correct_ratio)) %>%
  ungroup() %>%
  ggplot(aes(session, correct_ratio)) +
    geom_line(aes(color=participant))
```
```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarise(correct_ratio = mean(correct_ratio), .groups = "drop_last") %>%
  summarise(correct_ratio = mean(correct_ratio)) %>%
  ggplot(aes(session, correct_ratio)) +
    geom_line() + scale_y_continuous(limits = c(0,1))
```

```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarise(n_trials = max(n_trials)) %>%
  ggplot(aes(session, n_trials)) +
    geom_point() + geom_smooth(method = "lm")
```

```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarise(n_trials = max(n_trials), .groups = "drop_last") %>%
  summarise(mean_trial = mean(n_trials)) %>%
  ggplot(aes(session, mean_trial)) +
    geom_line() + scale_y_continuous(limits = c(2,11))
```

```{r}
df_results_remediation %>%
  group_by(session, n_items) %>%
  summarise(results_time = mean(results_time)) %>%
  ggplot(aes(session, results_time)) +
  geom_line() + facet_wrap(~n_items)
```

```{r}
df_results_remediation %>%
  filter(results_time < 400) %>%
  ggplot(aes(session, results_time)) +
    geom_point() + geom_smooth(method = "lm") + 
  facet_wrap(~n_items)
```

```{r}
df_results_remediation %>%
  ggplot(aes(session, results_trajectory)) +
    geom_point() + geom_smooth(method = "lm") + 
  facet_wrap(~n_items)
```

### 2021-01-10 scripts/run2-results-output.R

@@ -12,7 +12,6 @@ UNITY_DIR <- "E:/Google Drive/NUDZ/Projects/CDZ Karvina/VR-tasks/logy/2-pilot_VR
 participatns <- unique(df_sessions$id)
 
 exps <- load_participants_supermarket(UNITY_DIR, participatns)
-names(exps)
 df_results <- supermarket_results.participants(exps)
 
 df_results <- df_results %>% 
@@ -45,7 +44,6 @@ df_results %>%
   group_by(participant) %>%
   summarise(n = n(), sessions = length(unique(session)),
             timestamps = length(unique(timestamp)))
-
 
 df_results %>%
   group_by(session, participant) %>%

### 2021-01-22 functions/cdz-getters.R
Adds questionnaire loading and buffering

@@ -47,3 +47,14 @@ get_sheet_sessions <- function(preprocess = TRUE, overwrite = FALSE){
   df_sessions$use <- df_sessions$use == 1
   return(df_sessions)
 }
+
+get_sheet_questionnaire <- function(preprocess = TRUE){
+  GS_QUESTIONNAIRE <- "1oDGMtNYY_sGSQabzTfi3O18srZFcm-xxUWytqyryj0Y"
+  out <- googlesheets4::range_read(GS_QUESTIONNAIRE,
+                                                col_types = "iiccciiiiiiiicciiiiicc")
+  if(!preprocess) return(out)
+  out$used_memorization_technique <- recode(out$used_memorization_technique,
+                                            "Ano" = TRUE, "Ne" = FALSE, .default = NA)
+  
+  return(out)
+}

### 2021-01-22 scripts/buffer-online-tables.R

@@ -1,7 +1,9 @@
 df_demographics <- get_sheet_demographics()
 df_rbans <- get_sheet_rbans()
 df_ids <- get_sheet_ids()
+df_questionnaire <- get_sheet_questionnaire()
 
 write.table(df_ids, "information.csv", sep = ";", row.names = FALSE)
 write.table(df_demographics, "demographics.csv", sep = ";", row.names = FALSE)
 write.table(df_rbans, "rbans.csv", sep = ";", row.names = FALSE)
+write.table(df_questionnaire, "questionnaire.csv", sep = ";", row.names = FALSE)

### 2021-01-23 reports/questionnaire.Rmd
Adds questionnaire report

---
title: "Questionnaire "
author: "Lukáš 'hejtmy' Hejtmánek"
date: "22/01/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
df_questionnaire <- read.table("../questionnaire.csv", sep = ";", header = TRUE)
df_demographics <- read.table("../demographics.csv", sep = ";", header = TRUE)
df_questionnaire <- df_questionnaire %>%
  left_join(df_demographics, "rbansid" = "rbansid")
```

```{r}
df_questionnaire_long <- df_questionnaire %>%
  pivot_longer(cols = c(starts_with(c("vr", "paper")), -ends_with("feedback")),
               names_to = "questionnaire_section", values_to = "score") %>%
  separate(questionnaire_section, sep = "_", into = c("question_focus", "question_area"),
           extra="merge")
```

```{r}
df_questionnaire_long %>%
  ggplot(aes(y = score, fill = question_focus)) + 
    geom_boxplot() + 
  facet_wrap(~question_area)
```

```{r}
df_questionnaire_long %>%
  group_by(question_focus, question_area) %>%
  summarise(mean = mean(score)) %>%
  pivot_wider(names_from = question_focus, values_from = mean)
```

### 2021-01-24 functions/cdz-preprocess.R
Adds preprocessing function to calculate dimensions and mods the baselining

@@ -2,16 +2,17 @@ baseline_rbans <- function(df_rbans){
   df_rbans_baseline <- df_rbans %>%
     arrange(rbansid, trenink) %>% # order baseline TP VR
     group_by(rbansid) %>%
-    summarise_at(vars(testuceni:iq_celek), 
-                 list(vr = ~.x[3]-.x[1], tp = ~ .x[2]-.x[1])) %>%
+    summarise_at(vars(testuceni:iq_celek, starts_with("dim")), 
+                 list(VR = ~.x[3]-.x[1], TP = ~ .x[2]-.x[1])) %>%
     pivot_longer(!rbansid,
                  names_to = c(".value", "trenink"),
                  names_pattern = "(.+)_(.+)"
     )
   df_rbans_baseline <- df_rbans %>%
-    select(rbansid, diagnosis) %>%
+    select(rbansid, diagnosis, first_training, trenink, session) %>%
+    filter(session > 1) %>%
     distinct() %>%
-    right_join(df_rbans_baseline, by="rbansid")
+    right_join(df_rbans_baseline, by=c("rbansid", "trenink"))
   return(df_rbans_baseline)
 }
 
@@ -30,5 +31,15 @@ add_session_to_rbans <- function(df_rbans, df_demographics){
   df_rbans$session[df_rbans$first_training == df_rbans$trenink] <- 2
   df_rbans$session[df_rbans$trenink == "baseline"] <- 1
   df_rbans$session[is.na(df_rbans$first_training)] <- NA
+  return(df_rbans)
+}
+
+add_summaries_to_rbans <- function(df_rbans){
+  df_rbans <- df_rbans %>%
+    mutate(dim_kratkodobapamet = testuceni + testpameti,
+           dim_dlouhodobapamet = vybaveniseznamu + rekognice + vybavenipovidky + vybavenifigury,
+           dim_pozornost = opakovanicisel + symboly,
+           dim_rec = pojmenovaniobrazku + verbalnifluence,
+           dim_vizuoprostor = kopiefigury + orientaceprimek)
   return(df_rbans)
 }

### 2021-01-24 scripts/buffer-online-tables.R
Updates buffering

@@ -1,9 +1,15 @@
+source("functions/cdz-getters.R")
 df_demographics <- get_sheet_demographics()
-df_rbans <- get_sheet_rbans()
-df_ids <- get_sheet_ids()
-df_questionnaire <- get_sheet_questionnaire()
-
-write.table(df_ids, "information.csv", sep = ";", row.names = FALSE)
 write.table(df_demographics, "demographics.csv", sep = ";", row.names = FALSE)
+
+df_rbans <- get_sheet_rbans()
 write.table(df_rbans, "rbans.csv", sep = ";", row.names = FALSE)
+
+df_ids <- get_sheet_ids()
+write.table(df_ids, "information.csv", sep = ";", row.names = FALSE)
+
+df_questionnaire <- get_sheet_questionnaire()
 write.table(df_questionnaire, "questionnaire.csv", sep = ";", row.names = FALSE)
+
+df_sessions <- get_sheet_sessions()
+write.table(df_sessions, "sessions.csv", sep = ";", row.names = FALSE)

### 2021-01-24 reports/rbans-output.Rmd
Updates existing rbans and supermarket output

@@
 df_rbans <- add_session_to_rbans(df_rbans, df_demographics)
+
 df_rbans_long <- df_rbans %>%
@@
                  names_to = "subtest", values_to = "score")
+
 df_rbans_long <- df_rbans_long %>%
@@
 library(lme4)
+
 df_rbans %>%

### 2021-01-24 reports/supermarket-output.Rmd
Updates existing rbans and supermarket output

@@
 author: "Lukáš 'hejtmy' Hejtmánek"
-date: "10/01/2021"
+date: "`r Sys.Date()`"
 output: html_document
@@
 library(tidyverse)
-knitr::opts_chunk$set(echo = FALSE)
+library(lmerTest)
+library(lme4)
+knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message = FALSE)
 df_results <- read.table("../run2-results-supermarket-sessions.csv", sep = ";",
@@
 
-df_results <- filter(df_results, session <= 12)
+# First session was supposedly weird, and only few people did more than 12
+df_results <- filter(df_results, session <= 12, session > 1)
 
@@
 ```
+
+### Effect of session and number of items on trial time
+
+```{r}
+df_results_remediation %>%
+  filter(results_time < 400) %>%
+  ggplot(aes(session, results_time)) +
+    geom_jitter(height = 0.1, width = 0.2) +
+    scale_x_continuous(breaks = 2:12) +
+    geom_smooth(method = "lm") + 
+    facet_wrap(~n_items)
+```
+
+```{r}
+df_results_remediation %>%
+  group_by(session, n_items) %>%
+  summarise(results_time = mean(results_time)) %>%
+  ggplot(aes(session, y = results_time)) +
+    geom_line() +
+    facet_wrap(~n_items) +
+    scale_x_continuous(breaks = 2:12) +
+    labs(y = "average trial time")
+```
+
+```{r}
+lmer(results_time ~ session + n_items + (session | participant),
+  df_results_remediation) %>%
+  summary()
+```
+### Effect of session and number of items on correct ratio
 
@@
 ```
+
 ```{r}
@@
 ```{r}
+lmer(correct_ratio ~ session + n_items + (session | participant),
+  df_results_remediation) %>%
+  summary()
+```
+
+AS we could expect, the ratio stays the same. But participants generally achieve better times and higher difficulties, so that is not necessarily a problem.
+
+### Effect of session and number of items on trial trajectory
+
+```{r}
+df_results_remediation %>%
+  ggplot(aes(session, results_trajectory)) +
+    geom_jitter(width = 0.1, height = 0.3) +
+    scale_y_continuous(limits = c(0,750)) +
+    geom_smooth(method = "lm") + 
+    facet_wrap(~n_items) +
+  labs(y = "trial trajectory")
+```
+
+```{r}
+lmer(results_trajectory ~ session + n_items + (session | participant),
+  df_results_remediation) %>%
+  summary()
+```
+
+### Effect of session on maximum achieved difficulty
+```{r}
 df_results_remediation %>%
   group_by(session, participant) %>%
-  summarise(n_trials = max(n_trials)) %>%
-  ggplot(aes(session, n_trials)) +
-    geom_point() + geom_smooth(method = "lm")
+  summarise(n_trials = max(n_trials), .groups="drop") %>%
+  ggplot(aes(session, y = n_trials, color = participant)) +
+    geom_point()+
+    geom_smooth(method = "lm", se = FALSE) + 
+    facet_wrap(~participant) +
+    guides(color = FALSE) +
+    scale_x_continuous(breaks = 2:12) +
+    labs(y = "Maximum achieved difficulty")
 ```
@@
   group_by(session, participant) %>%
-  summarise(n_trials = max(n_trials), .groups = "drop_last") %>%
-  summarise(mean_trial = mean(n_trials)) %>%
-  ggplot(aes(session, mean_trial)) +
-    geom_line() + scale_y_continuous(limits = c(2,11))
+  summarise(n_trials = max(n_trials)) %>%
+  ggplot(aes(session, n_trials)) +
+    geom_jitter(aes(color=participant), height = 0.1, width = 0.2) +
+    geom_smooth(method = "lm") +
+    scale_x_continuous(breaks = 2:12) +
+    scale_y_continuous(breaks = 1:15) +
+    labs(y="maximum achieved difficulty") + guides(color=FALSE)
 ```
@@
 df_results_remediation %>%
-  group_by(session, n_items) %>%
-  summarise(results_time = mean(results_time)) %>%
-  ggplot(aes(session, results_time)) +
-  geom_line() + facet_wrap(~n_items)
+  group_by(session, participant) %>%
+  summarize(max_difficulty = max(n_items), .groups = "drop") %>%
+  lmer(max_difficulty ~ session  + (session||participant), data = .) %>%
+    VarCorr()
 ```
@@
 df_results_remediation %>%
-  filter(results_time < 400) %>%
-  ggplot(aes(session, results_time)) +
-    geom_point() + geom_smooth(method = "lm") + 
-  facet_wrap(~n_items)
+  group_by(session, participant) %>%
+  summarize(max_difficulty = max(n_items), .groups = "drop") %>%
+  lmer(max_difficulty ~ session  + (session | participant), data = .) %>%
+    summary()
 ```
-
-```{r}
-df_results_remediation %>%
-  ggplot(aes(session, results_trajectory)) +
-    geom_point() + geom_smooth(method = "lm") + 
-  facet_wrap(~n_items)
-```

### 2021-01-24 reports/results.Rmd
Creates final results section

@@
 ---
-title: "results"
+title: "Results"
 author: "Lukáš 'hejtmy' Hejtmánek"
@@
 ```{r setup, include=FALSE}
-knitr::optlibrary(tidyverse)
-knitr::opts_chunk$set(echo = FALSE)
+library(tidyverse)
+library(lmerTest)
+library(lme4)
+source("../functions/cdz-preprocess.R")
+knitr::opts_chunk$set(echo = FALSE, warning= FALSE)
+df_results <- read.table("../run2-results-supermarket-sessions.csv", sep = ";",
+                         header = TRUE)
 
-df_results <- read.table("../run2-results-supermarket-sessions.csv", sep = ";",
-                           header = TRUE)s_chunk$set(echo = TRUE)
+df_demographics <- read.table("../demographics.csv", sep = ";", header = TRUE)
+df_ids <- read.table("../information.csv", header = TRUE, sep = ";")
 
-df_ids <- read.table("../information.csv", sep = ";", header = TRUE)
-df_rbans <- read.table("../information.csv", sep = ";", header = TRUE)
+df_sessions <- read.table("../sessions.csv", header = TRUE, sep = ";")
+
+# Combine with demographics
+df_join <- df_demographics %>%
+  left_join(df_ids, by = "rbansid") %>%
+  select(rbansid, vrid) %>% 
+  filter(!is.na(rbansid) & !is.na(vrid))
+
+df_results <- df_results %>%
+  left_join(df_join, by = c("participant" = "vrid"))
+
+df_results <- df_results %>%
+  mutate(total_picked_items = n_correct_items + n_extra_items,
+         correct_ratio = n_correct_items/n_items,
+         extra_ratio = n_extra_items/n_items) %>%
+  group_by(participant, session) %>%
+  mutate(n_trials = n()) %>%
+  ungroup()
+
+# First session was supposedly weird, and only few people did more than 12
+df_results <- filter(df_results, session <= 12, session > 1)
+
+df_results_remediation <- filter(df_results, type == "remediation")
+df_results_test <- filter(df_results, type == "test")
+
+## RBANS ----
+df_rbans <- read.table("../rbans.csv", sep=";", header = TRUE) %>%
+  add_session_to_rbans(df_demographics) %>%
+  add_summaries_to_rbans()
+
+df_rbans_long <- df_rbans %>%
+    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
+                 names_to = "subtest", values_to = "score") %>%
+  group_by(session, subtest) %>%
+  mutate(z_score = scale(score)[,1])
+
+df_rbans_long <- df_rbans_long %>%
+  group_by(trenink, first_training, subtest) %>%
+  summarise(group_avg = mean(score, na.rm = TRUE),
+            group_z_avg = mean(z_score, na.rm = TRUE),
+            .groups="drop") %>%
+  right_join(df_rbans_long, by = c("trenink", "first_training", "subtest"))
 ```
+
+## Rbans
+
+```{r}
+df_rbans_long %>%
+  filter(grepl("dim_", subtest), !is.na(session)) %>%
+  ggplot(aes(subtest, z_score, fill = factor(session))) +
+    geom_boxplot() +
+    facet_wrap(~first_training) +
+    theme(axis.text.x =  element_text(angle = 45, vjust = 1, hjust = 1)) +
+    labs(y = "Scaled score", title = "Scaled score evolution based on session split by first training")
+
+df_rbans_long %>%
+  filter(grepl("dim_", subtest), !is.na(session)) %>%
+  ggplot(aes(subtest, z_score, fill = trenink)) +
+    geom_boxplot() +
+    facet_wrap(~session) +
+    theme(axis.text.x =  element_text(angle = 45, vjust = 1, hjust = 1)) +
+    labs(y = "Scaled score", title = "Scaled score evolution based on session split by session")
+```
+
+```{r}
+baseline_rbans(df_rbans) %>%
+    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
+                 names_to = "subtest", values_to = "score") %>%
+  filter(grepl("dim_", subtest), !is.na(session)) %>%
+  ggplot(aes(subtest, score, fill = factor(session))) +
+    geom_boxplot() +
+    geom_hline(yintercept = 0) +
+    facet_wrap(~first_training) +
+    theme(axis.text.x =  element_text(angle = 45, vjust = 1, hjust = 1)) +
+    labs(y = "Baseline change", title = "Change in score vs the baseline split by the first training")
+
+baseline_rbans(df_rbans) %>%
+    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
+                 names_to = "subtest", values_to = "score") %>%
+  filter(grepl("dim_", subtest), !is.na(session)) %>%
+  ggplot(aes(subtest, score, fill = trenink)) +
+    geom_boxplot() +
+    geom_hline(yintercept = 0) +
+    facet_wrap(~session) +
+    theme(axis.text.x =  element_text(angle = 45, vjust = 1, hjust = 1)) +
+    labs(y = "Baseline change", title = "Change in score vs the baseline split by the session")
+
+```
+
+## Supermarket improvement during the 6 weeks
+.
+VR - bylo by možné vzít průměr (1.
+sezení bylo víc zácvik a někteří dělali test, takže to ukazuje blbosti) 2.
+a 3 sezení a posledního a předposledního sezení a porovnat je?
+Myslím si, že tam je u většiny lidí posun, ale třeba o půl nebo jeden bod.
+Prostě je fakt minimální a potřebují pravděpodobně mnohem intenzivní trénink - liší se ti, co mají méně než 10 sezení od těch, kterí mají 10 a více?
+Žádné velké predikce bychom se nedělali - nejsou na to data a žádný jasný vztah tam nevidím teda.
+Očividně blbý efekt vidím u těch, co mega kolísají, Mohli bychom se tak i vyhnout načítání dat z domu (pokud je to prostě fakt těžký), jelikož ta úloha je mnohem složitější a připadá mi težké oddělit ty chyby mezi sebou a budou se míchat dohromady
+
+```{r}
+df_remediation_improvement <- df_results_remediation %>%
+  group_by(participant, session) %>%
+  summarise(max_diff  = max(n_items),
+            avg_ratio = mean(correct_ratio), .groups="drop_last") %>%
+  arrange(participant, session) %>%
+  summarise(ratio_improvement = mean(tail(avg_ratio, 2)) - mean(head(avg_ratio, 2)),
+            diff_improvement = mean(tail(max_diff, 2)) - mean(head(max_diff, 2)),
+            starting_diff = mean(head(max_diff, 2)), .groups = "drop")
+```
+
+Improvement in maximum achieved difficulty 
+```{r}
+df_remediation_improvement %>%
+  ggplot(aes(diff_improvement)) +
+  geom_histogram(binwidth = 1) +
+  geom_vline(xintercept = 0)
+```
+
+```{r}
+tab_improved <- table(sign(df_remediation_improvement$diff_improvement))
+as.data.frame(tab_improved) %>%
+  mutate(Var1 = c("worse performance", "same performance", "better performance"))
+```
+
+People are not spread equaly in the groups as measured by the chi.square
+```{r}
+chisq.test(tab_improved)
+```
+
+BUT! there is no significant difference in the number of people who got better (`r tab_improved[3]`) vs people who either performed worse  or did not improve (`r sum(tab_improved[1:2])`)
+```{r}
+chisq.test(table(df_remediation_improvement$diff_improvement > 0))
+```
+
+## adherence and feasibility 
+- počet absolvovaných VR sezení a jejich délka "jak dlouho u toho vydrželi" a výsledky dotazníků - jak je to bavilo, jestli by si to chtěli zopakovat a jestli jim to připadalo užitečné
+
+```{r}
+df_sessions %>%
+  group_by(id) %>%
+  summarise(n_sessions = max(session)) %>%
+  group_by(n_sessions) %>%
+  summarise(n = n())
+```
+
+There is no variability in the number of VR sessions - 17/20 people did 12 or 13 sessions, so there is no point in searching for the effect of number of sessions.
+
+```{r}
+
+```
+
+## Mixed model random effect predicting the rbans performance
+
+```{r}
+lmer_difficulty_session <- df_results_remediation %>%
+  group_by(session, participant) %>%
+  summarize(max_difficulty = max(n_items), .groups = "drop") %>%
+  lmer(max_difficulty ~ session  + (session | participant), data = .)
+```
+
+Modelling the supermarket with mixed effect modelling gives us base trial difficulty of `r fixef(lmer_difficulty_session)[1]` and improvement of `r fixef(lmer_difficulty_session)[2 q]` per session.
+But it also models individual improvement and base performance.
+That is in the table below.
+Some participants have overall better base performance and some simply improve better or worse from this baseline.
+We can use these metrics to predict the RBANS performance change.
+
+```{r}
+ranef(lmer_difficulty_session)$participant %>%
+  arrange(session) %>%
+  knitr::kable(col.names = c("Base performance change", "Improvement change"))
+```
+
+```{r}
+random_coeffs <- df_results_remediation %>%
+  group_by(session, rbansid) %>%
+  summarize(max_difficulty = max(n_items), .groups = "drop") %>%
+  lmer(max_difficulty ~ session  + (session | rbansid), data = .) %>%
+  ranef() %>% .$rbansid
+
+colnames(random_coeffs) <- c("intercept", "session_slope")
+random_coeffs$rbansid <- rownames(random_coeffs)
+
+df_rbans_randcoef <- df_rbans_long %>%
+  filter(trenink == "VR", grepl("dim_", subtest), !is.na(score)) %>%
+  left_join(random_coeffs, by = "rbansid") %>%
+  select(-starts_with("group"), -diagnosis)
+
+df_rbans_randcoef_wide_score <- df_rbans_randcoef %>%
+  select(-z_score) %>%
+  pivot_wider(names_from = "subtest", values_from = "score") %>%
+  filter(!is.na(intercept))
+
+df_rbans_randcoef_wide_zscore <- df_rbans_randcoef %>%
+  select(-score) %>%
+  pivot_wider(names_from = "subtest", values_from = "z_score") %>%
+  filter(!is.na(intercept))
+
+df_rbans_randcoef_baseline_wide <- baseline_rbans(df_rbans) %>%
+    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
+                 names_to = "subtest", values_to = "score") %>%
+  filter(trenink == "VR", grepl("dim_", subtest), !is.na(score)) %>%
+  left_join(random_coeffs, by = "rbansid") %>%
+  select(-starts_with("group"), -diagnosis) %>%
+  filter(!is.na(intercept)) %>%
+  pivot_wider(names_from = "subtest", values_from = "score")
+
+```
+
+These results are kinda challenging to explain and I am not sure if they are correct :D But the thing is ...
+when modelling the supermarket performance as an effect of session, we get those individual "intercepts" (basically default skill) and "session_slope" (rate of change - some people learn faster than others) - viz paragraph above.
+I then use these individual estimates to predict rbans score!
+Therefore predicting RBANS standardized scores by the "default" skill in supermarket and the "rate of improvement in supermarket" and also the session(arguably participants doing the VR in 2nd iteration should be generally better than those doing it in the 1st).
+Below are the results for individual rbans scales (those are scaled per session (B has different scaling than C))
+
+```{r}
+glm(dim_dlouhodobapamet ~ intercept + session_slope + factor(session), data = df_rbans_randcoef_wide_zscore) %>%
+  summary()
+
+glm(dim_kratkodobapamet  ~ intercept + session_slope + factor(session), data = df_rbans_randcoef_wide_zscore) %>%
+  summary()
+
+glm(dim_rec ~ intercept + session_slope + factor(session), data = df_rbans_randcoef_wide_zscore) %>%
+  summary()
+
+glm(dim_pozornost ~ intercept + session_slope + factor(session), data = df_rbans_randcoef_wide_zscore) %>%
+  summary()
+
+glm(dim_vizuoprostor   ~ intercept + session_slope + factor(session), data = df_rbans_randcoef_wide_zscore) %>%
+  summary()
+
+```
+
+What we can see is that the base individual performance (and although it SOUNDS like BASELINE, it really is not for some participants, especially if intercept is correlated with slope - which in our case is at r=0.31) predicts RBANS score for short and long term memory!!!
+The better the participants do in supermarket, the better they do in the following RBANS.
+
+WARNING WARNING WARNING!!!!
+I am absolutely NOT SURE I can do it this way :D it just occured to me and it beautifully corresponds to what we might expect happening, so there you go.
+But I'll ponder of the matter of affairs a bit longer.
+Also, it does NOT take into consideration the rbans baseline!
+E.g.
+there is certainly some cross correlation - people who do well in RBANS do well in supermarket as well.
+Personally I believe that is the case, rather than supermarket actually changing something.
+I tried to run the model on baseline changes, but it is generally non significant for those valid scales and becomes significant for the OTHER scales.
+BUT the issue is with the generally incomparability of the RBANS A-B-C versions, and therefore we dunno if the A-C decrease of 2 points in long term memory is actually INCREASE in performance, as C is so much more challenging.
+That would require complete rescaling of RBANS and we DO NOT have enough peeps to do so.
+
+## dodatek - mapování strategií
+
+- dle dotazníku použilo ve VR jen 5 osob z 25 nějakou konkrétní strategii - proto by mohl mít význam strategy-base approach.
+a frekvence a intenzita tréninku se nám asi tolik neukazuje, když nevidíme zlepšení ani po 24 sezení?
+ale možná by mohla mít význam vyšší frekvence
+
+Tomu asi nerozumím :()

### 2021-01-24 reports/supermarket-output.Rmd
Updates graphs with proper axes

@@
   group_by(session, participant) %>%
-  summarise(n_trials = max(n_trials), .groups="drop") %>%
-  ggplot(aes(session, y = n_trials, color = participant)) +
+  summarise(max_difficulty = max(n_items), .groups="drop") %>%
+  ggplot(aes(session, y = max_difficulty, color = participant)) +
     geom_point()+
-    geom_smooth(method = "lm", se = FALSE) + 
+    geom_smooth(method = "lm") + 
     facet_wrap(~participant) +
@@
   group_by(session, participant) %>%
-  summarise(n_trials = max(n_trials)) %>%
-  ggplot(aes(session, n_trials)) +
+  summarise(max_difficulty = max(n_items)) %>%
+  ggplot(aes(session, max_difficulty)) +
     geom_jitter(aes(color=participant), height = 0.1, width = 0.2) +
@@
   summarize(max_difficulty = max(n_items), .groups = "drop") %>%
-  lmer(max_difficulty ~ session  + (session||participant), data = .) %>%
+  lmer(max_difficulty ~ session  + (session|participant), data = .) %>%
     VarCorr()

### 2021-02-12 functions/cdz-getters.R
Fixes sheet getters

@@ -1,4 +1,5 @@
 get_sheet_ids <- function(preprocess = TRUE, overwrite = FALSE){
+  GS_RUN2_DEMOGRAPHICS_RBANS <- "1qMdiLYY7EIbNvoRsE5knjBB24zXT7hgJNUCmwMX7IwY"
   df_ids <- googlesheets4::range_read(GS_RUN2_DEMOGRAPHICS_RBANS, sheet = "ID")
   if(!preprocess) return(df_ids)
   colnames(df_ids) <- tolower(colnames(df_ids))
@@ -25,6 +26,7 @@ get_sheet_demographics <- function(preprocess = TRUE, overwrite = FALSE){
 }
 
 get_sheet_rbans <- function(preprocess = TRUE, overwrite = FALSE){
+  GS_RUN2_DEMOGRAPHICS_RBANS <- "1qMdiLYY7EIbNvoRsE5knjBB24zXT7hgJNUCmwMX7IwY"
   df_rbans <- googlesheets4::range_read(GS_RUN2_DEMOGRAPHICS_RBANS,
                                         sheet = "rbans")
   if(!preprocess) return(df_rbans)

### 2021-02-12 reports/questionnaire.Rmd
Updates questionnaire reports

@@
 library(tidyverse)
-knitr::opts_chunk$set(echo = TRUE)
-df_questionnaire <- read.table("../questionnaire.csv", sep = ";", header = TRUE)
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+df_questionnaire <- read.table("../questionnaire.csv", sep = ";", header = TRUE) %>%
+  mutate_at(vars(starts_with(c("vr", "paper", "supermarket"))), function(x){ifelse(x == 6, NA, x)})
 df_demographics <- read.table("../demographics.csv", sep = ";", header = TRUE)
+
 df_questionnaire <- df_questionnaire %>%
-  left_join(df_demographics, "rbansid" = "rbansid")
+  left_join(df_demographics, c("rbansid" = "rbansid"))
 ```
@@
     geom_boxplot() + 
-  facet_wrap(~question_area)
+    facet_wrap(~question_area) +
+    theme(legend.position="bottom")
 ```
@@
 ```{r}
+df_temp <- df_questionnaire_long %>%
+  group_by(question_area, question_focus) %>%
+  summarise(mean = mean(score, na.rm = TRUE)) %>%
+  pivot_wider(names_from = question_focus, values_from = mean)
+
 df_questionnaire_long %>%
-  group_by(question_focus, question_area) %>%
-  summarise(mean = mean(score)) %>%
-  pivot_wider(names_from = question_focus, values_from = mean)
+  group_by(question_area) %>%
+  summarise(t.test_p = t.test(score~question_focus)$p.value) %>%
+  right_join(df_temp, by = "question_area") %>%
+  knitr::kable(digits = 3)
 ```

### 2021-02-12 scripts/buffer-online-tables.R
Cleans preprocessing scripts

@@ -1,3 +1,4 @@
+library(tidyverse)
 source("functions/cdz-getters.R")
 df_demographics <- get_sheet_demographics()
 write.table(df_demographics, "demographics.csv", sep = ";", row.names = FALSE)

### 2021-02-12 scripts/run2-results-output.R

@@ -37,8 +37,6 @@ df_results %>%
   select(participant, timestamp) %>%
   distinct()
 
-View(df_results)
-
 df_results %>%
   filter(!is.na(session)) %>%
   group_by(participant) %>%

### 2021-02-12 reports/results.Rmd
Slight changes t results reports

@@
 
-## Mixed model random effect predicting the rbans performance
+## Mixed model RBANS
+```{r}
+df_rbans_conditions <- filter(df_rbans, session != 1)
+summary(manova(as.matrix(select(df_rbans_conditions, starts_with("dim_"))) ~ session + trenink, df_rbans_conditions))
+```
+
+Predicting IQ celek
+
+```{r}
+lmer_iq_celek <- lmer(iq_celek ~ trenink + factor(session) + (1|rbansid), data = df_rbans_conditions)
+summary(lmer_iq_celek)
+```
+```{r}
+summary(lmer(dim_kratkodobapamet ~ trenink + factor(session) + (1|rbansid), data = df_rbans_conditions))
+summary(lmer(dim_dlouhodobapamet ~ trenink + factor(session) + (1|rbansid), data = df_rbans_conditions))
+summary(lmer(dim_pozornost ~ trenink + factor(session) + (1|rbansid), data = df_rbans_conditions))
+summary(lmer(dim_rec ~ trenink + factor(session) + (1|rbansid), data = df_rbans_conditions))
+summary(lmer(dim_vizuoprostor ~ trenink + factor(session) + (1|rbansid), data = df_rbans_conditions))
+```
+
+## Mixed model random effect predicting the rbans performance with supermarket performance
 
@@
   summary()
-
 ```
@@
 That would require complete rescaling of RBANS and we DO NOT have enough peeps to do so.
-
-## dodatek - mapování strategií
-
-- dle dotazníku použilo ve VR jen 5 osob z 25 nějakou konkrétní strategii - proto by mohl mít význam strategy-base approach.
-a frekvence a intenzita tréninku se nám asi tolik neukazuje, když nevidíme zlepšení ani po 24 sezení?
-ale možná by mohla mít význam vyšší frekvence
-
-Tomu asi nerozumím :()

### 2021-02-12 reports/supermarket-output.Rmd
Slight changes t results reports

@@
   ggplot(aes(session, correct_ratio)) +
-    geom_line() + scale_y_continuous(limits = c(0,1))
+    geom_line() + scale_y_continuous(limits = c(0, 1))
+```
+
+```{r}
+df_results_remediation %>%
+  ggplot(aes(session, correct_ratio)) +
+  geom_point() + geom_smooth(method = "lm") +
+  facet_wrap(~n_items)
+
+df_results_remediation %>%
+  filter(n_items > 6) %>%
+  ggplot(aes(session, correct_ratio, color = factor(n_items))) +
+  geom_jitter(width = 0.25) +
+  geom_smooth(aes(color = "all"), method = "lm")
 ```
@@
   ggplot(aes(session, y = max_difficulty, color = participant)) +
-    geom_point()+
+    geom_point() +
     geom_smooth(method = "lm") +

### 2021-02-12 reports/preprocessing-demographics.Rmd
Adds preprocessing report

---
title: "preprocessing"
author: "Lukáš 'hejtmy' Hejtmánek"
date: "12/02/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lmerTest)
library(lme4)
source("../functions/cdz-preprocess.R")
knitr::opts_chunk$set(echo = TRUE)
```

Loading the already prepared files. THe results are loaded and analyzed results form the supermarket, the demographics are from the online google sheet at [ID CDZ](https://docs.google.com/spreadsheets/d/1qMdiLYY7EIbNvoRsE5knjBB24zXT7hgJNUCmwMX7IwY/edit#gid=0) from sheet demografie, the ids are data from the same file and sheet ID, the rbans from the same file sheet RBANS, the sessions are used to determine timestamps for each individual session and are loaded from this google sheet [sessions](https://docs.google.com/spreadsheets/d/1rFm8QnjGw3BQuFfMvGiLUa5hMvg3-8iTP8h5DGMZLlc/edit#gid=0). The files are loaded from prepared csv files generated by scripts in the `scripts/` folder. The df_results are already joined with the df_sessions from the preprocessing stage (see file `scripts/run2-results-output.R`)
```{r loading}
df_results <- read.table("../run2-results-supermarket-sessions.csv", sep = ";",
                         header = TRUE)

df_demographics <- read.table("../demographics.csv", sep = ";", header = TRUE)
df_ids <- read.table("../information.csv", header = TRUE, sep = ";")
df_sessions <- read.table("../sessions.csv", header = TRUE, sep = ";")
df_rbans <- read.table("../rbans.csv", sep=";", header = TRUE)
```

## Data joining and combining

### Supermarket

The supermarket has `r length(unique(df_results$participant))` participants before join.
```{r adding demographics to supermarket}
# Combine with demographics
df_join <- df_demographics %>%
  left_join(df_ids, by = "rbansid") %>%
  select(rbansid, vrid) %>% 
  filter(!is.na(rbansid) & !is.na(vrid))
df_results <- df_results %>%
  left_join(df_join, by = c("participant" = "vrid"))
rm(df_join)
```

And it has `r length(unique(df_results$participant))` after the join. We then add new variables such as correct ratio etc.

```{r adding supermarket metrics}
df_results <- df_results %>%
  mutate(total_picked_items = n_correct_items + n_extra_items,
         correct_ratio = n_correct_items/n_items,
         extra_ratio = n_extra_items/n_items) %>%
  group_by(participant, session) %>%
  mutate(n_trials = n()) %>%
  ungroup()
```

### Rbans
We first add a session to rbans data based on the df_demographics sheet. The RBANS sheet does NOT have session value, it only has if participant did TP or VR prior to that version, so we need to figure out what was their first and second training.

```{r}
df_rbans <- add_session_to_rbans(df_rbans, df_demographics)
```

Then we calculate the individual scores for each category. These are prefixed by `dim_` prefix, where the original scores are prefixed with `iq_`.
```{r}
df_rbans <- add_summaries_to_rbans(df_rbans)
```

## Outlier and participant removal

We remove the first session and all sessions above 12 from the supermarket data

```{r}
# First session was supposedly weird, and only few people did more than 12
df_results <- filter(df_results, session <= 12, session > 1)
```

And filter for different versions of supermarket tests. Remediation used different verion of the settings than test verion
```{r}
df_results_remediation <- filter(df_results, type == "remediation")
df_results_test <- filter(df_results, type == "test")
```

Usually participants have one fewer session due to us discarding the session number 1, but overall they all have 12 sessions completed.

```{r}
df_results_remediation %>%
  group_by(participant) %>%
  summarise(n_sessions = length(unique(session)),
            max_session = max(session)) %>%
    pivot_longer(cols = c(max_session, n_sessions)) %>%
    ggplot(aes(participant, value, fill = name)) +
      geom_col(position = "dodge") +
      coord_flip() + labs(title = "Number of valid sessions and maximum achieved session")
```

```{r}
df_results_remediation %>%
  group_by(participant) %>%
  summarise(n_sessions = length(unique(session)),
            max_session = max(session)) %>%
    pivot_longer(cols = c(max_session, n_sessions)) %>%
    group_by(name) %>%
    count(value) %>%
    knitr::kable(col.names = c("", "value", "Number of participants"), 
                 caption = "Number of participants with given number of valid sessions")
```

## Final sample

The final RBANS counts look like this
```{r rbansfinal}
df_rbans %>%
  group_by(rbansid) %>%
  summarise(n_sessions = sum(!is.na(testuceni)), .groups="drop") %>%
  count(n_sessions) %>%
  knitr::kable(col.names =  c("RBANS completed", "Number of subjects"))

df_rbans %>%
  group_by(trenink) %>%
  summarise(n_sessions = sum(!is.na(testuceni))) %>%
  knitr::kable(col.names =  c("trenink", "Number of subjects"))

df_rbans %>%
  group_by(session) %>%
  summarise(n_sessions = sum(!is.na(testuceni))) %>%
  knitr::kable(col.names =  c("Session", "Number of subjects"))
```

Combining the rbans with supermarket to get the "cross" results - only people who have both the supermarket data and the rbans data to acompany it

```{r}
df_check_complete <- df_results_remediation %>%
  select(participant, rbansid) %>%
  distinct %>%
  left_join(filter(df_rbans, trenink == "VR")) %>%
  filter(!is.na(testuceni)) %>%
  select(participant, rbansid, session)
```

That is `r nrow(df_check_complete)` people who have both.

```{r}
df_check_complete %>%
  group_by(session) %>%
  count() %>%
  knitr::kable(caption = "Number of peopel who have VR in each session")
```

### 2021-02-12 reports/interactive-rbans.Rmd
Updates results

@@
 author: "Lukáš 'hejtmy' Hejtmánek"
-date: "25/03/2020"
+date: "`r Sys.Date()`"
 output: 
@@
 knitr::opts_chunk$set(echo = FALSE)
-opts_knit$set(root.dir = "../")
+#opts_knit$set(root.dir = "../")
+```
 
+```{r}
 source("../functions/cdz-loading-pilot.R")
@@
 ```{r loading}
-df_ids <- get_sheet_ids()
-df_demographics <- get_sheet_demographics()
-df_sessions <- get_sheet_sessions()
-df_rbans <- get_sheet_rbans()
+df_results <- read.table("../run2-results-supermarket-sessions.csv", sep = ";",
+                         header = TRUE)
+df_demographics <- read.table("../demographics.csv", sep = ";", header = TRUE)
+df_ids <- read.table("../information.csv", header = TRUE, sep = ";")
+df_sessions <- read.table("../sessions.csv", header = TRUE, sep = ";")
+df_rbans <- read.table("../rbans.csv", sep=";", header = TRUE) %>%
+  add_session_to_rbans(df_demographics) %>%
+  add_summaries_to_rbans()
 ```
@@
 ```{r preprocessing}
-df_rbans <- add_session_to_rbans(df_rbans, df_demographics)
 df_rbans_long <- df_rbans %>%
@@
                  names_to = "subtest", values_to = "score")
+
 df_rbans_long <- df_rbans_long %>%
   group_by(trenink, first_training, subtest) %>%
-  summarise(group_avg = mean(score, na.rm = TRUE)) %>%
-  ungroup() %>%
+  summarise(group_avg = mean(score, na.rm = TRUE), .groups="drop") %>%
   right_join(df_rbans_long, by = c("trenink", "first_training", "subtest"))
 
-df_rbans_long <- df_rbans_long %>%
-  arrange(rbansid, session)
+df_rbans_long <- arrange(df_rbans_long, rbansid, session)
+df_rbans_long <- mutate(df_rbans_long, fac_session = factor(session))
 
@@
 plot_ly(shared_rbans, x = ~session, y = ~scaled_score) %>%
-  add_trace(type = "box",  color = ~as.factor(session),
+  add_trace(type = "box",  color = ~fac_session,
             hoverinfo = "y", showlegend = TRUE, boxmean = TRUE) %>%
@@
 plot_ly(shared_rbans, x = ~session, y = ~scaled_score) %>%
-  add_trace(type = "scatter", x=~session, y = ~scaled_score,
-            mode = "lines+markers", split = ~rbansid) %>%
+  add_trace(type = "scatter", x=~fac_session, y = ~scaled_score,
+            mode = "lines", split = ~rbansid, color = ~rbansid) %>%
+  add_markers(x = ~jitter(as.numeric(session), amount = 0.02), y = ~scaled_score, color = ~rbansid) %>%
   layout(showlegend = FALSE, autosize = TRUE, height = 500)
@@
   filter(first_training == "TP") %>%
-  plot_ly(x= ~session, y = ~scaled_score) %>%
-   add_trace(type = "box",  color = ~as.factor(session),
+  plot_ly(x= ~fac_session, y = ~scaled_score) %>%
+    add_trace(type = "box",  color = ~fac_session,
             hoverinfo = "y", showlegend = TRUE, boxmean = TRUE) %>%

### 2021-02-12 reports/preprocessing-demographics.Rmd
Updates results

@@
 The final RBANS counts look like this
-```{r rbansfinal}
+```{r rbansfinal, message=FALSE}
 df_rbans %>%
@@
   knitr::kable(col.names =  c("Session", "Number of subjects"))
+
+df_rbans %>%
+  filter(session == 1) %>%
+  group_by(first_training) %>%
+  summarise(n_sessions = sum(!is.na(testuceni))) %>%
+  knitr::kable(col.names =  c("First Training", "Number of subjects"))
 ```

### 2021-02-12 reports/results.Rmd
Updates results

@@
 
-```{r}
-
-```
-
 ## Mixed model RBANS
@@
 
-Modelling the supermarket with mixed effect modelling gives us base trial difficulty of `r fixef(lmer_difficulty_session)[1]` and improvement of `r fixef(lmer_difficulty_session)[2 q]` per session.
+Modelling the supermarket with mixed effect modelling gives us base trial difficulty of `r fixef(lmer_difficulty_session)[1]` and improvement of `r fixef(lmer_difficulty_session)[2]` per session.
 But it also models individual improvement and base performance.

### 2021-02-18 reports/results.Rmd
Updates results slightly

@@
     pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
-                 names_to = "subtest", values_to = "score") %>%
+                 names_to = "subtest",
+                 values_to = "score") %>%
   filter(grepl("dim_", subtest), !is.na(session)) %>%
@@
     theme(axis.text.x =  element_text(angle = 45, vjust = 1, hjust = 1)) +
-    labs(y = "Baseline change", title = "Change in score vs the baseline split by the first training")
+    labs(y = "Baseline change",
+         title = "Change in score vs the baseline split by the first training")
 
@@
     theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
-    labs(y = "Baseline change", title = "Change in score vs the baseline split by the session")
-
+    labs(y = "Baseline change",
+         title = "Change in score vs the baseline split by the session")
 ```

### 2021-02-18 reports/manuscript.Rmd
First hit at the manuscript

---
title: "manuscript"
author: "Lukáš 'hejtmy' Hejtmánek"
date: "15/02/2021"
output: html_document
---
```{r setup, echo = FALSE}
library(tidyverse)
library(lmerTest)
library(lme4)
library(helprs)
library(papaja)
source("../functions/cdz-preprocess.R")
knitr::opts_chunk$set(echo = FALSE, warning= FALSE)
df_results <- read.table("../run2-results-supermarket-sessions.csv", sep = ";",
                         header = TRUE)

df_demographics <- read.table("../demographics.csv", sep = ";", header = TRUE)
df_ids <- read.table("../information.csv", header = TRUE, sep = ";")

df_sessions <- read.table("../sessions.csv", header = TRUE, sep = ";")

# Combine with demographics
df_results <- df_demographics %>%
  left_join(df_ids, by = "rbansid") %>%
  select(rbansid, vrid) %>% 
  filter(!is.na(rbansid) & !is.na(vrid)) %>%
  right_join(df_results, by = c("vrid" = "participant")) %>%
  mutate(participant = vrid) %>%
  select(-vrid)

df_results <- df_results %>%
  mutate(total_picked_items = n_correct_items + n_extra_items,
         correct_ratio = n_correct_items/n_items,
         extra_ratio = n_extra_items/n_items) %>%
  group_by(participant, session) %>%
  mutate(n_trials = n(), 
         max_difficulty = max(n_items)) %>%
  ungroup()

# First session was supposedly weird, and only few people did more than 12
df_results <- filter(df_results, session <= 12, session > 1)

df_results_remediation <- filter(df_results, type == "remediation")
df_results_test <- filter(df_results, type == "test")

## RBANS ----
df_rbans <- read.table("../rbans.csv", sep = ";", header = TRUE) %>%
  add_session_to_rbans(df_demographics) %>%
  add_summaries_to_rbans()

df_rbans_long <- df_rbans %>%
    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
                 names_to = "subtest", values_to = "score") %>%
  group_by(session, subtest) %>%
  mutate(z_score = scale(score)[,1])

df_rbans_long <- df_rbans_long %>%
  group_by(trenink, first_training, subtest) %>%
  summarise(group_avg = mean(score, na.rm = TRUE),
            group_z_avg = mean(z_score, na.rm = TRUE),
            .groups="drop") %>%
  right_join(df_rbans_long, by = c("trenink", "first_training", "subtest"))

## Questionnaire ----
df_questionnaire <- read.table("../questionnaire.csv", sep = ";", header = TRUE) %>%
  mutate_at(vars(starts_with(c("vr", "paper", "supermarket"))), function(x){ifelse(x == 6, NA, x)})

df_questionnaire <- df_questionnaire %>%
  left_join(df_demographics, c("rbansid" = "rbansid"))

```

## Demographics
```{r}
good_participants <- df_rbans %>% 
  group_by(rbansid) %>%
  filter(!is.na(testpameti)) %>%
  summarise(n = n()) %>%
  filter(n >= 2) %>%
  pull(rbansid)

df_demographics_good <- df_demographics %>%
  filter(rbansid %in% good_participants)
table(df_demographics_good$gender)['male']
mean_and_sd_report(df_demographics[df_demographics$gender == "male", "age"])
```

A total of `r nrow(df_demographics)` participants were recruited. Only those participants who completed at least one intervention session were included in the subsequent analyses: `r nrow(df_demographics_good)` in total, `r table(df_demographics_good$gender)['male']` male (`r mean_and_sd_report(df_demographics[df_demographics$gender == "male", "age"])`), female `r table(df_demographics_good$gender)['female']` (`r mean_and_sd_report(df_demographics[df_demographics$gender == "female", "age"])`).

Demografická tabulka s průměry délky onemocnění, věkem, vzděláním atp - případně vytvořím sama, můžeš třeba jen vysypat ta data (a nebo to taky udělám)
```{r}
df_demographics_good %>%
  select(age, ilness_duration_years) %>%
  pivot_longer(everything()) %>%
  group_by(name) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            sd = mean(value, na.rm = TRUE)) %>%
  knitr::kable(digits = 3)

df_demographics_good %>%
  count(diagnosis) %>%
  knitr::kable()

df_demographics_good %>%
  count(education) %>%
  knitr::kable
```

Adherence rate – potřebujeme info o tom, kolik lidí bylo zahrnuto do studie (splnili kritéria), kolik lidí odpadlo v průběhu VR  nebo TP, kolik lidí odmítlo začít VR/TP - já bych doplnila důvody odpadu

## Questionnaire

```{r}
df_temp <- df_questionnaire_long %>%
  group_by(question_area, question_focus) %>%
  summarise(mean = mean_and_sd_report(score)) %>%
  pivot_wider(names_from = question_focus, values_from = mean)

df_questionnaire_long <- df_questionnaire %>%
  pivot_longer(cols = c(starts_with(c("vr", "paper")), -ends_with("feedback")),
               names_to = "questionnaire_section", values_to = "score") %>%
  separate(questionnaire_section, sep = "_", into = c("question_focus", "question_area"),
           extra="merge")

df_questionnaire_long %>%
  group_by(question_area) %>%
  summarise(t.test = apa_print(t.test(score~question_focus))$statistic) %>%
  right_join(df_temp, by = "question_area") %>%
  select(question_area, paper, vr, t.test)
  knitr::kable(digits = 3, caption = "")

t_questionnaire_repeat <- t.test(df_questionnaire$vr_would_repeat, df_questionnaire$paper_would_repeat)
```

The questionnaire aimed at assesing patients subjective perception of the intervention in terms of difficulty, fun or improvement indicate no significant difference between the paper tests and the VR tests in either of the five categories (see table XXX). Although the patients seem to give a slight edge to the paper tests in terms of repeatability `r apa_print(t_questionnaire_repeat)$statistic`. This can be due to arguably (XXXX higher demands of the VR tests or lack of social interaction ??) and is addressed in the discussion.

## Supermarket

Supermarket – reportovat zlepšení v difficulty achieved  (celkový graf) a v čase trialů - linear mixed models (možná se podívat na ten součet N correct za session + correct ration pro úroveň 6, 7, 8)

RBANS – dle pokynů Ivety a dle počtů lidí se mrknout na vliv pořadí a verze RBANS a tréninku

RBANS – dodat prosím srovnání (i když je jasné, že je nesignifikantní), dodat tabulku s průměry před a po a SD a non-signifikance, graf změny (ten, co je asi nejvíc vypovídající, change vůči baseline?)

### 2021-02-19 reports/functions/reporting.R
Adds reporting mixed models

@@ -1,0 +1,10 @@
+report_mixed_effect <- function(model, pred){
+  coefs <- summary(model)$coefficients
+  res <- coefs[pred, ]
+  txt <- paste0("$b = ", round(res[1], 2), "$, ",
+                "95% CI [", round(res[1] - 1.96 * res[2], 2), ", ",
+                round(res[1] + 1.96 * res[2], 2), "]", ", ",
+                "$t(", round(res[3], 2),") = ", round(res[4], 2), "$, ",
+                "$p = ", papaja::printp(res[5]), "$")
+  return(txt)
+}

### 2021-02-19 functions/cdz-preprocess.R
Adds dimension celek

@@ -40,6 +40,8 @@ add_summaries_to_rbans <- function(df_rbans){
            dim_dlouhodobapamet = vybaveniseznamu + rekognice + vybavenipovidky + vybavenifigury,
            dim_pozornost = opakovanicisel + symboly,
            dim_rec = pojmenovaniobrazku + verbalnifluence,
-           dim_vizuoprostor = kopiefigury + orientaceprimek)
+           dim_vizuoprostor = kopiefigury + orientaceprimek,
+           dim_celek = dim_kratkodobapamet + dim_dlouhodobapamet + dim_pozornost +
+             dim_rec + dim_vizuoprostor)
   return(df_rbans)
 }

### 2021-02-19 reports/manuscript.Rmd
First version of manuscript results

@@
 ---
-```{r setup, echo = FALSE}
+```{r setup, echo = FALSE, message = FALSE}
 library(tidyverse)
@@
 source("../functions/cdz-preprocess.R")
-knitr::opts_chunk$set(echo = FALSE, warning= FALSE)
+source("functions/reporting.R")
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
 df_results <- read.table("../run2-results-supermarket-sessions.csv", sep = ";",
@@
 
+good_participants <- df_rbans %>% 
+  group_by(rbansid) %>%
+  filter(!is.na(testpameti)) %>%
+  summarise(n = n()) %>%
+  filter(n >= 2) %>%
+  pull(rbansid)
+
+df_rbans <- df_rbans %>%
+  filter(rbansid %in% good_participants)
+
 df_rbans_long <- df_rbans %>%
@@
 df_questionnaire <- read.table("../questionnaire.csv", sep = ";", header = TRUE) %>%
-  mutate_at(vars(starts_with(c("vr", "paper", "supermarket"))), function(x){ifelse(x == 6, NA, x)})
-
-df_questionnaire <- df_questionnaire %>%
+  mutate_at(vars(starts_with(c("vr", "paper", "supermarket"))), 
+            function(x){ifelse(x == 6, NA, x)}) %>%
   left_join(df_demographics, c("rbansid" = "rbansid"))
-
-```
-
-## Demographics
-```{r}
-good_participants <- df_rbans %>% 
-  group_by(rbansid) %>%
-  filter(!is.na(testpameti)) %>%
-  summarise(n = n()) %>%
-  filter(n >= 2) %>%
-  pull(rbansid)
 
@@
   filter(rbansid %in% good_participants)
-table(df_demographics_good$gender)['male']
-mean_and_sd_report(df_demographics[df_demographics$gender == "male", "age"])
 ```
+
+## Methods
+Due to missing standardization procedures for calculating RBANS IQ scores in version C and an arguable difference between the three versions, we have opted to use the raw scores and not the standard metrics in RBANS related calculations.
+We normalized our raw scores in each RBANS domain for each version separately.
+As our models take RBANS version into account to control for potential raw score differences between different versions and because of the normalization procedure, we consider this approach in our scenario to be more statistically powerful.
+
+## Demographics
 
@@
 Demografická tabulka s průměry délky onemocnění, věkem, vzděláním atp - případně vytvořím sama, můžeš třeba jen vysypat ta data (a nebo to taky udělám)
+
 ```{r}
@@
   count(education) %>%
-  knitr::kable
+  knitr::kable()
 ```
@@
 ```{r}
-df_temp <- df_questionnaire_long %>%
-  group_by(question_area, question_focus) %>%
-  summarise(mean = mean_and_sd_report(score)) %>%
-  pivot_wider(names_from = question_focus, values_from = mean)
-
 df_questionnaire_long <- df_questionnaire %>%
@@
 
+df_temp <- df_questionnaire_long %>%
+  group_by(question_area, question_focus) %>%
+  summarise(mean = mean_and_sd_report(score)) %>%
+  pivot_wider(names_from = question_focus, values_from = mean)
+
 df_questionnaire_long %>%
@@
   right_join(df_temp, by = "question_area") %>%
-  select(question_area, paper, vr, t.test)
+  select(question_area, paper, vr, t.test) %>%
   knitr::kable(digits = 3, caption = "")
@@
 
-Supermarket – reportovat zlepšení v difficulty achieved  (celkový graf) a v čase trialů - linear mixed models (možná se podívat na ten součet N correct za session + correct ration pro úroveň 6, 7, 8)
+```{r}
+df_results_remediation %>%
+  group_by(session, n_items) %>%
+  summarise(correct_ratio = mean_and_sd_report(correct_ratio),
+            time = mean_and_sd_report(results_time),
+            trajectory = mean_and_sd_report(results_trajectory)) %>%
+  filter(session == 2 | session == 12) %>%
+  knitr::kable(caption = "Select what might be relevant or what to aggregate together")
+```
 
-RBANS – dle pokynů Ivety a dle počtů lidí se mrknout na vliv pořadí a verze RBANS a tréninku
+```{r}
+df_results_remediation %>%
+  select(rbansid, session, max_difficulty) %>%
+  distinct() %>%
+  ggplot(aes(session, max_difficulty)) + 
+    geom_jitter(height = 0, width = 0.15) +
+    geom_smooth(method = "lm") +
+    scale_x_continuous(breaks = seq(2,12,1)) + theme_apa() +
+    labs(y = "Maximum difficulty achieved", x = "Session", 
+         title = "Maximum difficulty achieved as an effect of session")
 
-RBANS – dodat prosím srovnání (i když je jasné, že je nesignifikantní), dodat tabulku s průměry před a po a SD a non-signifikance, graf změny (ten, co je asi nejvíc vypovídající, change vůči baseline?)
+lmer_diff_session <- df_results_remediation %>%
+  select(rbansid, session, max_difficulty) %>%
+  distinct() %>%
+  lmer(max_difficulty ~ session + (1|rbansid), data = .)
+
+lmer_time_session_trial <- lmer(results_time ~ session + n_items + (1|participant), data = df_results_remediation)
+
+lmer_trajectory_session_trial <- lmer(results_trajectory ~ session + n_items + (1|participant), data = df_results_remediation)
+```
+
+Using mixed effect modeling we looked at how patients learned the task as the cognitive trainign progressed.
+We observed that participants were continously able to improve and proceed to more difficult trials as the training progressed `r report_mixed_effect(lmer_diff_session, "session")`.
+
+As the trajectory and time of trials is dependent both on learning as well as task difficulty (more items take longer to pick up), we modelled the trial time and trajectory with both session and trial difficulty as a predictor.
+We  observed that participants improved in both these measures as cognitive training progressed, seeing decrease in trial trajectories `r report_mixed_effect(lmer_trajectory_session_trial, "session")` and trial times `r report_mixed_effect(lmer_time_session_trial, "session")` with each new session.
+
+## RBANS
+
+```{r}
+df_rbans %>%
+  group_by(session, trenink) %>%
+  summarise(mean_celek = mean_and_sd_report(dim_celek),
+            n = sum(!is.na(dim_celek))) %>%
+  knitr::kable()
+```
+
+```{r}
+df_rbans_long %>%
+  filter(grepl("dim_", subtest)) %>%
+  mutate(session = session -1) %>%
+  ggplot(aes(subtest, z_score, fill = trenink)) + 
+  geom_boxplot() +
+  facet_wrap(~session) +
+  theme_apa() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = c(0.5,1), legend.direction = "horizontal") +
+  labs(title = "Standardized scores of rbans dimensions in first and second session\nWill edit labels and colors if we keep this")
+
+baseline_rbans(df_rbans) %>%
+    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
+                 names_to = "subtest", values_to = "score") %>%
+  filter(grepl("dim_", subtest)) %>%
+  mutate(session = session -1) %>%
+  ggplot(aes(subtest, score, fill = trenink)) +
+    geom_boxplot() +
+    geom_hline(yintercept = 0) +
+    facet_wrap(~session) +
+    theme_apa() +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = c(0.5,1), legend.direction = "horizontal") +
+    labs(y = "Baseline change",
+         title = "Change in score vs the baseline split by the session\nWill edit labels and colors if we keep this")
+```
+
+```{r}
+df_rbans_no_baseline <- filter(df_rbans, session != 1)
+```
+
+```{r}
+temp_mixed_func <- function(varname){
+  out <- df_rbans_long %>%
+    filter(subtest == varname, session > 1) %>%
+    lmer(z_score ~ trenink + factor(session) + (1|rbansid), data = .)
+  return(out)
+}
+
+lmer_celek <- temp_mixed_func("dim_celek")
+lmer_kratkodobapamet <- temp_mixed_func("dim_kratkodobapamet")
+lmer_dlouhodobapamet <- temp_mixed_func("dim_dlouhodobapamet")
+lmer_pozornost <-temp_mixed_func("dim_pozornost")
+lmer_rec <- temp_mixed_func("dim_rec")
+lmer_vizuoprostor <- temp_mixed_func("dim_vizuoprostor")
+
+dims <- c("dim_celek", "dim_kratkodobapamet", "dim_dlouhodobapamet",
+          "dim_pozornost", "dim_rec", "dim_vizuoprostor")
+res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), 2)})
+knitr::kable(as.data.frame(res), caption = "Trenink as a predictor of RBANS performance")
+```
+
+Using linear mixed effect modeling we explored the effect of the intervention as well as the session on the RBANS scores with the participant as a random effect to remove individual differences in RBANS performance.
+We have not found any effect, neither positive nor negative, of intervention type (see table XXX).
+We have only found a negative effect of session on the normalized total RBANS score `r report_mixed_effect(lmer_celek, 3)` with people at the end of the study (thrid RBANS, both interventions completed) scoring marginally worse than in previous tests.
+This can be due to XXXXX

### 2021-02-20 reports/manuscript.Rmd
Adds manuscript report

@@
          title = "Maximum difficulty achieved as an effect of session")
+```
 
+```{r mixed models vSST results}
 lmer_diff_session <- df_results_remediation %>%
@@
 lmer_trajectory_session_trial <- lmer(results_trajectory ~ session + n_items + (1|participant), data = df_results_remediation)
+
+lmer_correct_session_6_9 <- lmer(correct_ratio ~ session + n_items + (1|participant), data = filter(df_results_remediation, n_items >= 6))
 ```
@@
 As the trajectory and time of trials is dependent both on learning as well as task difficulty (more items take longer to pick up), we modelled the trial time and trajectory with both session and trial difficulty as a predictor.
-We  observed that participants improved in both these measures as cognitive training progressed, seeing decrease in trial trajectories `r report_mixed_effect(lmer_trajectory_session_trial, "session")` and trial times `r report_mixed_effect(lmer_time_session_trial, "session")` with each new session.
+We  observed that participants improved in both these measures as cognitive training progressed, seeing decrease in trial trajectories (`r report_mixed_effect(lmer_trajectory_session_trial, "session")`) and trial times (`r report_mixed_effect(lmer_time_session_trial, "session")`) with each new session.
+
+One of the other metric we explored previously and found to be indicative of cognitive performance (PLECHATA CS PSY) was the vSST correct ratio.
+As the correct ratio is dependent on task difficulty (more difficult trials lead to higher performance decline), and as we learned in our previous work that patients only start to struggle after 5 item difficulty, we only analyzed this metric in trials beginning with difficulty of six items.
+Modeling the correct ratio as a function of session and task difficulty, we observed that indeed the task difficulty significantly decreases the performance in this metric (`r report_mixed_effect(lmer_correct_session_6_9, "n_items")`), but number of completed sessions had no effect (`r report_mixed_effect(lmer_correct_session_6_9, "session")`).
+
+XXX - discussion??
+Drop ?
+Patients did eventually improve in the vSST, as suggested by the upward trend in achieved difficulty with progressing sessions, and due to the nature of the task (higher difficulty is only triggered if the correct ratio of the current one is perfect) this must mean that patients must have had slightly improved in this metric as well, although this change was much more gradual and is "noised XXX" by the number of trial repetitions patients did.
 
@@
   group_by(session, trenink) %>%
-  summarise(mean_celek = mean_and_sd_report(dim_celek),
-            n = sum(!is.na(dim_celek))) %>%
+  summarise_at(vars(starts_with("dim")), list(desc = mean_and_sd_report,
+            n = ~sum(!is.na(.x)))) %>%
+  mutate(number = dim_kratkodobapamet_n) %>%
+  select(-ends_with("_n")) %>%
+  rename_with(~gsub("dim_(.*)_desc", "\\1", .x)) %>%
   knitr::kable()
@@
   labs(title = "Standardized scores of rbans dimensions in first and second session\nWill edit labels and colors if we keep this")
-
-baseline_rbans(df_rbans) %>%
-    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
-                 names_to = "subtest", values_to = "score") %>%
-  filter(grepl("dim_", subtest)) %>%
-  mutate(session = session -1) %>%
-  ggplot(aes(subtest, score, fill = trenink)) +
-    geom_boxplot() +
-    geom_hline(yintercept = 0) +
-    facet_wrap(~session) +
-    theme_apa() +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = c(0.5,1), legend.direction = "horizontal") +
-    labs(y = "Baseline change",
-         title = "Change in score vs the baseline split by the session\nWill edit labels and colors if we keep this")
 ```
@@
     filter(subtest == varname, session > 1) %>%
-    lmer(z_score ~ trenink + factor(session) + (1|rbansid), data = .)
+    lmer(z_score ~ trenink*factor(session) + (1|rbansid), data = .)
   return(out)

### 2021-02-23 reports/participant.Rmd
Adds basic participant report and knitter

---
author: "Lukáš 'hejtmy' Hejtmánek"
date: "`r Sys.Date()`"
output: html_document
params:
  participant: NA
  data_dir: NA
title: "`r paste0('Report pro ', params$participant)`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(brainvr.supermarket)
library(tidyverse)
source("../functions/cdz-loading-pilot.R")
source("../functions/cdz-analysis.R")
source("../functions/cdz-getters.R")
par <- list(data_dir = "E:/Google Drive/NUDZ/Projects/CDZ Karvina/VR-tasks/logy/2-pilot_VR-pen-paper/",
               participant = "bohdan")
df_sessions <- read.table("../sessions.csv", header = TRUE, sep = ";")
exps <- load_participant_supermarket(par$data_dir, par$participant)

results <- supermarket_results.participant(exps)

results <- results %>% 
  separate(timestamp, sep = "-", into = c("hour", "minute", "second", "day", "month", "year"), remove = FALSE) %>% 
  mutate(day = gsub("[0]([0-9])", "\\1", day),
         month = gsub("0([0-9])", "\\1", month)) %>%
  unite("date", c(day, month, year), sep = ".") %>%
  select(-c(hour, minute, second))

results <- results %>%
  left_join(filter(df_sessions, task == "supermarket", use),
            by = c("participant" = "id", "date" = "date")) %>%
  filter(!is.na(session)) %>%
  mutate(date.posix = as.POSIXct(date, format="%d.%m.%Y"))

results <- results %>%
  mutate(total_picked_items = n_correct_items + n_extra_items,
         correct_ratio = n_correct_items/n_items,
         extra_ratio = n_extra_items/n_items) %>%
  group_by(participant, session) %>%
  mutate(n_trials = n()) %>%
  ungroup()

colors <- c("#63873a", "#f3f7e9", "#25aae1", "#81c6e2")
```

## Supermarket

V rámci studie jste absolvoval/a `r length(unique(results$timestamp))` sezení. První `r format(min(results$date.posix), "%d.%m.%Y")` a poslední `r format(max(results$date.posix), "%d.%m.%Y")`.

V tomto grafu vidíte jaké maximální úrovně (počet předmětů na nákupním seznamu) jste v supermarketu v daný den dosáhl/a a jaká byla ten den vaše průměrná úspěšnost.

```{r}
results %>%
  group_by(date.posix) %>%
  summarise(max = max(n_items),
            correct = mean(correct_ratio)) %>%
  ggplot(aes(date.posix, max)) +
    geom_line(aes(y = correct, color= "Úspěšnost"), size = 2) +
    geom_line(aes(y = max/11, color = "Dosažená úroveň"), size = 2) +
    scale_y_continuous(labels = function(x) x*11,
                       sec.axis = sec_axis(~.*100, name = "Úspěšnost %"),
                       limits=c(0,1), breaks = seq(0,1,1/11)) +
    geom_point(aes(y=correct), color = colors[3], size = 5) +
    geom_point(aes(y=max/11), color = colors[1], size = 5) +
    scale_colour_manual(values = colors[c(2,4)]) + 
    theme_bw() +
    labs(title = "Maximální dosažená úroveň", x = "", y = "Úroveň") +
    theme(legend.position = "bottom")
```

XXX - problematické předměty

### 2021-02-23 reports/knitting-participant.R

@@ -1,0 +1,10 @@
+library(withr)
+library(helprs)
+UNITY_DIR =  "E:/Google Drive/NUDZ/Projects/CDZ Karvina/VR-tasks/logy/2-pilot_VR-pen-paper/"
+parameters = list(data_dir = UNITY_DIR, participant = "bohdan")
+with_locale(new = c('LC_CTYPE' = helprs::get_czech_platform_locale(),
+                    'LC_TIME' = 'Czech'),
+            rmarkdown::render("reports/participant.Rmd",
+                              params = parameters,
+                              output_dir = "reports/participants/",
+                              output_file = parameters$participant))

### 2021-02-24 reports/manuscript.Rmd
Edits manuscript

@@
 df_sessions <- read.table("../sessions.csv", header = TRUE, sep = ";")
-
-# Combine with demographics
-df_results <- df_demographics %>%
-  left_join(df_ids, by = "rbansid") %>%
-  select(rbansid, vrid) %>% 
-  filter(!is.na(rbansid) & !is.na(vrid)) %>%
-  right_join(df_results, by = c("vrid" = "participant")) %>%
-  mutate(participant = vrid) %>%
-  select(-vrid)
-
-df_results <- df_results %>%
-  mutate(total_picked_items = n_correct_items + n_extra_items,
-         correct_ratio = n_correct_items/n_items,
-         extra_ratio = n_extra_items/n_items) %>%
-  group_by(participant, session) %>%
-  mutate(n_trials = n(), 
-         max_difficulty = max(n_items)) %>%
-  ungroup()
-
-# First session was supposedly weird, and only few people did more than 12
-df_results <- filter(df_results, session <= 12, session > 1)
-
-df_results_remediation <- filter(df_results, type == "remediation")
-df_results_test <- filter(df_results, type == "test")
 
@@
 
+## SUPERMARKET ------
+df_results <- df_demographics %>%
+  left_join(df_ids, by = "rbansid") %>%
+  select(rbansid, vrid) %>% 
+  filter(!is.na(rbansid) & !is.na(vrid)) %>%
+  right_join(df_results, by = c("vrid" = "participant")) %>%
+  mutate(participant = vrid) %>%
+  select(-vrid)
+
+df_results <- df_results %>%
+  mutate(total_picked_items = n_correct_items + n_extra_items,
+         correct_ratio = n_correct_items/n_items,
+         extra_ratio = n_extra_items/n_items) %>%
+  group_by(participant, session) %>%
+  mutate(n_trials = n(), 
+         max_difficulty = max(n_items)) %>%
+  ungroup()
+
+# First session was supposedly weird, and only few people did more than 12
+df_results <- filter(df_results, session <= 12, session > 1)
+df_results <- filter(df_results, rbansid %in% good_participants)
+df_results_remediation <- filter(df_results, type == "remediation")
+df_results_test <- filter(df_results, type == "test")
+
 ## Questionnaire ----
@@
   summarise(mean = mean(value, na.rm = TRUE),
-            sd = mean(value, na.rm = TRUE)) %>%
+            sd = sd(value, na.rm = TRUE)) %>%
   knitr::kable(digits = 3)
@@
 
+### Different diagnoses
+
+```{r}
+df_demographics_good %>%
+  mutate(diagnosis = sapply(diagnosis, function(x){
+    if(grepl("F3.*", x)) return("affective")
+    if(grepl("F2.*", x)) return("schizophrenia")
+  })) %>%
+  count(diagnosis, first_training) %>%
+  pivot_wider(names_from = diagnosis, values_from = n) %>%
+  knitr::kable()
+
+df_rbans_long %>%
+  filter(grepl("dim_", subtest)) %>%
+  ggplot(aes(subtest, z_score, fill=diagnosis)) +
+  geom_boxplot()
+
+df_diag_difference <- df_rbans_long %>%
+  filter(grepl("dim_", subtest)) %>%
+  group_by(subtest) %>%
+  summarise(t_test = apa_print(t.test(z_score~diagnosis))$statistic, 
+            .groups = "drop")
+
+df_rbans_long %>%
+  filter(grepl("dim_", subtest)) %>%
+  group_by(subtest, diagnosis) %>%
+  summarise(mean = mean(z_score, na.rm = TRUE)) %>%
+  pivot_wider(names_from = diagnosis, values_from = mean) %>%
+  right_join(df_diag_difference, by = "subtest") %>%
+  knitr::kable(digits = 3)
+```
+
 Adherence rate – potřebujeme info o tom, kolik lidí bylo zahrnuto do studie (splnili kritéria), kolik lidí odpadlo v průběhu VR  nebo TP, kolik lidí odmítlo začít VR/TP - já bych doplnila důvody odpadu
@@
                names_to = "questionnaire_section", values_to = "score") %>%
-  separate(questionnaire_section, sep = "_", into = c("question_focus", "question_area"),
+  separate(questionnaire_section, sep = "_",
+           into = c("question_focus", "question_area"),
            extra="merge")
@@
 
-t_questionnaire_repeat <- t.test(df_questionnaire$vr_would_repeat, df_questionnaire$paper_would_repeat)
+t_questionnaire_repeat <- t.test(df_questionnaire$vr_would_repeat,
+                                 df_questionnaire$paper_would_repeat)
 ```
 
-The questionnaire aimed at assesing patients subjective perception of the intervention in terms of difficulty, fun or improvement indicate no significant difference between the paper tests and the VR tests in either of the five categories (see table XXX).
+The questionnaire aimed at assessing patients’ subjective perception of the intervention in terms of difficulty, fun or improvement indicate no significant difference between the standard treatment and the VEs program in either of the five categories (see table XXX).
 Although the patients seem to give a slight edge to the paper tests in terms of repeatability `r apa_print(t_questionnaire_repeat)$statistic`.
-This can be due to arguably (XXXX higher demands of the VR tests or lack of social interaction ??) and is addressed in the discussion.
 
@@
 
-Using mixed effect modeling we looked at how patients learned the task as the cognitive trainign progressed.
-We observed that participants were continously able to improve and proceed to more difficult trials as the training progressed `r report_mixed_effect(lmer_diff_session, "session")`.
+Using mixed effect modeling we looked at how patients learned the task as the cognitive training progressed.
+We observed that participants were continuously able to improve and proceed to more difficult trials as the training progressed `r report_mixed_effect(lmer_diff_session, "session")`.
 
-As the trajectory and time of trials is dependent both on learning as well as task difficulty (more items take longer to pick up), we modelled the trial time and trajectory with both session and trial difficulty as a predictor.
+As the trajectory and time of trials is dependent both on learning as well as task difficulty (more items take longer to pick up), we modeled the trial time and trajectory with both session and trial difficulty as a predictor.
 We  observed that participants improved in both these measures as cognitive training progressed, seeing decrease in trial trajectories (`r report_mixed_effect(lmer_trajectory_session_trial, "session")`) and trial times (`r report_mixed_effect(lmer_time_session_trial, "session")`) with each new session.
@@
   filter(grepl("dim_", subtest)) %>%
-  mutate(session = session -1) %>%
-  ggplot(aes(subtest, z_score, fill = trenink)) + 
+  mutate(session = paste0("session ", session - 1),
+         fac_subtest = factor(subtest, levels = c("dim_celek", "dim_kratkodobapamet",
+                                                  "dim_dlouhodobapamet", "dim_rec",
+                                                  "dim_pozornost", "dim_vizuoprostor"))) %>%
+  ggplot(aes(fac_subtest, z_score, fill = trenink)) +
     geom_boxplot() +
-  facet_wrap(~session) +
+    facet_wrap(~session,  strip.position = "bottom") +
+    scale_x_discrete(labels = c("dim_celek" = "Total", "dim_kratkodobapamet" = "Immediate memory", 
+    "dim_vizuoprostor" = "Visuospatial abilities", "dim_rec" = "Speech", "dim_pozornost" = "Attention",
+    "dim_dlouhodobapamet" = "Long term memory")) +
+    scale_fill_discrete(labels = c("baseline", "TP" = "Standard treatment",
+                                   "VR" = "VEs program")) +
     theme_apa() +
@@
           legend.position = c(0.5,1), legend.direction = "horizontal") +
-  labs(title = "Standardized scores of rbans dimensions in first and second session\nWill edit labels and colors if we keep this")
+    labs(x = "", y = "Standardized score",
+         title = "Standardized scores of RBANS cognitive domains",
+         fill = "")
 ```
@@
     filter(subtest == varname, session > 1) %>%
-    lmer(z_score ~ trenink*factor(session) + (1|rbansid), data = .)
+    lmer(z_score ~ trenink + factor(session) + (1|rbansid), data = .)
   return(out)
@@
 res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), 2)})
-knitr::kable(as.data.frame(res), caption = "Trenink as a predictor of RBANS performance")
+knitr::kable(as.data.frame(res),
+             caption = "Trenink as a predictor of RBANS performance. Coefficients are for VR in contrast to TP (negative = VR does worse)")
 ```
 
-Using linear mixed effect modeling we explored the effect of the intervention as well as the session on the RBANS scores with the participant as a random effect to remove individual differences in RBANS performance.
+Using linear mixed effect modeling we explored the effect of the intervention as well as the session on the RBANS scores with the participant as a random effect to remove within subject differences in RBANS performance.
 We have not found any effect, neither positive nor negative, of intervention type (see table XXX).
-We have only found a negative effect of session on the normalized total RBANS score `r report_mixed_effect(lmer_celek, 3)` with people at the end of the study (thrid RBANS, both interventions completed) scoring marginally worse than in previous tests.
+We have only found a negative effect of session on the normalized total RBANS score `r report_mixed_effect(lmer_celek, 3)` with people at the end of the study (third RBANS, both interventions completed) scoring marginally worse than in previous tests.
 This can be due to XXXXX

### 2021-02-27 reports/manuscript.Rmd
Updates manuscript

@@
 
+We have observed that patients suffering from schizophrenia had significantly worse baseline RBANS performance than patietns with affective disorders (see table XXX).
+This was one of the reasons we opted for the linear mixed modelling in our subsequent analyses as they should be able to control for the effect of diagnosis.
+
 ```{r}
@@
 df_rbans_long %>%
-  filter(grepl("dim_", subtest)) %>%
+  filter(grepl("dim_", subtest), session == 1) %>%
   group_by(subtest, diagnosis) %>%
-  summarise(mean = mean(z_score, na.rm = TRUE)) %>%
-  pivot_wider(names_from = diagnosis, values_from = mean) %>%
+  summarise(m = mean_and_sd_report(z_score, type = "parentheses")) %>%
+  pivot_wider(names_from = diagnosis, values_from = m) %>%
   right_join(df_diag_difference, by = "subtest") %>%
@@
   group_by(question_area, question_focus) %>%
-  summarise(mean = mean_and_sd_report(score)) %>%
+  summarise(mean = mean_and_sd_report(score, type = "parentheses")) %>%
   pivot_wider(names_from = question_focus, values_from = mean)
@@
   group_by(session, n_items) %>%
-  summarise(correct_ratio = mean_and_sd_report(correct_ratio),
-            time = mean_and_sd_report(results_time),
-            trajectory = mean_and_sd_report(results_trajectory)) %>%
+  summarise(correct_ratio = mean_and_sd_report(correct_ratio, type="parentheses"),
+            time = mean_and_sd_report(results_time, type="parentheses"),
+            trajectory = mean_and_sd_report(results_trajectory, type="parentheses")) %>%
   filter(session == 2 | session == 12) %>%
@@
 lmer_time_session_trial <- lmer(results_time ~ session + n_items + (1|participant), data = df_results_remediation)
-
 lmer_trajectory_session_trial <- lmer(results_trajectory ~ session + n_items + (1|participant), data = df_results_remediation)
-
 lmer_correct_session_6_9 <- lmer(correct_ratio ~ session + n_items + (1|participant), data = filter(df_results_remediation, n_items >= 6))
@@
   group_by(session, trenink) %>%
-  summarise_at(vars(starts_with("dim")), list(desc = mean_and_sd_report,
+  summarise_at(vars(starts_with("dim")), list(
+            desc = ~mean_and_sd_report(.x, type = "parentheses"),
             n = ~sum(!is.na(.x)))) %>%
@@
 This can be due to XXXXX
+
+```{r session model explanation,eval = FALSE}
+temp_mixed_func <- function(varname){
+  out <- df_rbans_long %>%
+    filter(subtest == varname) %>%
+    lmer(z_score ~ factor(session) + (1|rbansid), data = .)
+  return(out)
+}
+
+lmer_celek <- temp_mixed_func("dim_celek")
+lmer_kratkodobapamet <- temp_mixed_func("dim_kratkodobapamet")
+lmer_dlouhodobapamet <- temp_mixed_func("dim_dlouhodobapamet")
+lmer_pozornost <-temp_mixed_func("dim_pozornost")
+lmer_rec <- temp_mixed_func("dim_rec")
+lmer_vizuoprostor <- temp_mixed_func("dim_vizuoprostor")
+
+dims <- c("dim_celek", "dim_kratkodobapamet", "dim_dlouhodobapamet",
+          "dim_pozornost", "dim_rec", "dim_vizuoprostor")
+res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), 2)})
+knitr::kable(as.data.frame(res),
+             caption = "Trenink as a predictor of RBANS performance. Coefficients are for VR in contrast to TP (negative = VR does worse)")
+
+df_rbans_long %>%
+  filter(subtest == "dim_celek") %>%
+  mutate(session = paste0("session ", session - 1)) %>%
+  ggplot(aes(session, z_score, fill = trenink)) +
+    geom_boxplot() +
+    geom_jitter(position = position_dodge(width = 0.5)) +
+    scale_fill_discrete(labels = c("baseline", "TP" = "Standard treatment", "VR" = "VEs program")) +
+    geom_hline(yintercept = 0.07) +
+    theme_apa() +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1),
+          legend.position = c(0.5,1), legend.direction = "horizontal") +
+    labs(x = "", y = "Standardized score",
+         title = "Standardized scores of RBANS cognitive domains",
+         fill = "")
+
+df_rbans_long %>%
+  filter(subtest == "dim_celek") %>%
+  ggplot(aes(session, z_score, group = rbansid)) + 
+    geom_line() + geom_point(aes(color = trenink), size = 3)
+
+df_rbans_long %>%
+  filter(subtest == "dim_celek") %>%
+  group_by(session) %>%
+  summarise(mean_and_sd_report(score))
+```

### 2021-03-09 reports/manuscript.Rmd
Manuscript update

@@
 
+n_vr <- sum(!is.na(df_questionnaire$vr_benefit))
+n_paper <- sum(!is.na(df_questionnaire$paper_fun))
+
 t_questionnaire_repeat <- t.test(df_questionnaire$vr_would_repeat,
@@
 The questionnaire aimed at assessing patients’ subjective perception of the intervention in terms of difficulty, fun or improvement indicate no significant difference between the standard treatment and the VEs program in either of the five categories (see table XXX).
+`r n_vr` participants answered the questions about the VR portion of the program and `n_paper` about the standard treatment.
 Although the patients seem to give a slight edge to the paper tests in terms of repeatability `r apa_print(t_questionnaire_repeat)$statistic`.
@@
 lmer_dlouhodobapamet <- temp_mixed_func("dim_dlouhodobapamet")
-lmer_pozornost <-temp_mixed_func("dim_pozornost")
+lmer_pozornost <- temp_mixed_func("dim_pozornost")
 lmer_rec <- temp_mixed_func("dim_rec")
@@
 knitr::kable(as.data.frame(res),
-             caption = "Trenink as a predictor of RBANS performance. Coefficients are for VR in contrast to TP (negative = VR does worse)")
+             caption = "Trenink as a predictor of RBANS performance. 
+             Coefficients are for VR in contrast to TP (negative = VR does worse)")
+
 ```
@@
 This can be due to XXXXX
+
+```{r rbans czech norms, eval=FALSE}
+df_rbans_long %>%
+  filter(grepl("iq_", subtest)) %>%
+  ggplot(aes(subtest, score, fill = factor(session))) +
+    geom_boxplot() +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1),
+          legend.position  = "top", legend.direction = "horizontal")
+
+df_rbans_long %>%
+  filter(grepl("dim_", subtest)) %>%
+  ggplot(aes(subtest, score, fill = factor(session))) +
+    geom_boxplot() +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1),
+          legend.position  = "top", legend.direction = "horizontal")
+
+df_rbans_long %>%
+  filter(!grepl("(iq|dim)_", subtest)) %>%
+  ggplot(aes(subtest, score, fill = factor(session))) +
+    geom_boxplot() +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1),
+          legend.position  = "top", legend.direction = "horizontal")
+
+temp_mixed_func <- function(varname){
+  out <- df_rbans_long %>%
+    filter(subtest == varname, session > 1) %>%
+    lmer(score ~ trenink + factor(session) + (1|rbansid), data = .)
+  return(out)
+}
+
+temp_glm_func <- function(varname){
+  out <- df_rbans_long %>%
+    filter(subtest == varname) %>%
+    glm(score ~ session, data = .)
+  return(out)
+}
+
+summary(temp_mixed_func("iq_celek"))
+summary(temp_glm_func("iq_rec"))
+```
 
@@
 ```
+
+```{r}
+df_rbans_long %>%
+  filter(grepl("iq_", subtest)) %>%
+  mutate(session = paste0("session ", session - 1)) %>%
+  ggplot(aes(subtest, score, fill = trenink)) +
+    geom_boxplot()
+```

### 2021-03-11 reports/manuscript.Rmd
updates manuscript

@@
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+
+CDZ_COLORS <- c("#63873a", "#f3f7e9", "#25aae1", "#81c6e2")
+
 df_results <- read.table("../run2-results-supermarket-sessions.csv", sep = ";",
@@
 df_diag_difference <- df_rbans_long %>%
-  filter(grepl("dim_", subtest)) %>%
+  filter(grepl("iq_", subtest)) %>%
   group_by(subtest) %>%
-  summarise(t_test = apa_print(t.test(z_score~diagnosis))$statistic, 
+  summarise(t_test = apa_print(t.test(score ~ diagnosis))$statistic, 
             .groups = "drop")
@@
 df_rbans_long %>%
-  filter(grepl("dim_", subtest), session == 1) %>%
+  filter(grepl("iq_", subtest), session == 1) %>%
   group_by(subtest, diagnosis) %>%
-  summarise(m = mean_and_sd_report(z_score, type = "parentheses")) %>%
+  summarise(m = mean_and_sd_report(score, type = "parentheses")) %>%
   pivot_wider(names_from = diagnosis, values_from = m) %>%
@@
   knitr::kable(digits = 3)
+
+df_rbans %>%
+  group_by()
+
 ```
@@
 
-n_vr <- sum(!is.na(df_questionnaire$vr_benefit))
+n_vr <- sum(!is.na(df_questionnaire$vr_fun))
 n_paper <- sum(!is.na(df_questionnaire$paper_fun))
@@
 The questionnaire aimed at assessing patients’ subjective perception of the intervention in terms of difficulty, fun or improvement indicate no significant difference between the standard treatment and the VEs program in either of the five categories (see table XXX).
-`r n_vr` participants answered the questions about the VR portion of the program and `n_paper` about the standard treatment.
+`r n_vr` participants answered the questions about the VR portion of the program and `r n_paper` about the standard treatment.
 Although the patients seem to give a slight edge to the paper tests in terms of repeatability `r apa_print(t_questionnaire_repeat)$statistic`.
@@
     geom_jitter(height = 0, width = 0.15) +
-    geom_smooth(method = "lm") +
-    scale_x_continuous(breaks = seq(2,12,1)) + theme_apa() +
-    labs(y = "Maximum difficulty achieved", x = "Session", 
-         title = "Maximum difficulty achieved as an effect of session")
+    geom_smooth(method = "lm", fill = CDZ_COLORS[4], color = CDZ_COLORS[3]) +
+    scale_x_continuous(breaks = seq(2,12,1)) + 
+    theme_apa() +
+    labs(y = "Maximum difficulty achieved", x = "Session")
+ggsave("figures/fig1-session-difficulty.png",  width = 8, height = 6)
 ```
@@
 lmer_correct_session_6_9 <- lmer(correct_ratio ~ session + n_items + (1|participant), data = filter(df_results_remediation, n_items >= 6))
+
+lmer_ratio_session <- df_results_remediation %>%
+  lmer(correct_ratio ~ session + n_items + (1|rbansid), data = .)
+summary(lmer_ratio_session)
 ```
@@
   group_by(session, trenink) %>%
-  summarise_at(vars(starts_with("dim")), list(
+  summarise_at(vars(starts_with("iq_")), list(
             desc = ~mean_and_sd_report(.x, type = "parentheses"),
             n = ~sum(!is.na(.x)))) %>%
-  mutate(number = dim_kratkodobapamet_n) %>%
+  mutate(number = iq_kratkodobapamet_n) %>%
   select(-ends_with("_n")) %>%
-  rename_with(~gsub("dim_(.*)_desc", "\\1", .x)) %>%
+  rename_with(~gsub("iq_(.*)_desc", "\\1", .x)) %>%
   knitr::kable()
@@
 df_rbans_long %>%
-  filter(grepl("dim_", subtest)) %>%
+  filter(grepl("iq_", subtest)) %>%
   mutate(session = paste0("session ", session - 1),
-         fac_subtest = factor(subtest, levels = c("dim_celek", "dim_kratkodobapamet",
-                                                  "dim_dlouhodobapamet", "dim_rec",
-                                                  "dim_pozornost", "dim_vizuoprostor"))) %>%
-  ggplot(aes(fac_subtest, z_score, fill = trenink)) +
+         fac_subtest = factor(subtest, levels = c("iq_celek", "iq_kratkodobapamet",
+                                                  "iq_dlouhodobapamet", "iq_rec",
+                                                  "iq_pozornost", "iq_vizuoprostorschopnosti"))) %>%
+  ggplot(aes(fac_subtest, score, fill = trenink)) +
     geom_boxplot() +
     facet_wrap(~session,  strip.position = "bottom") +
-    scale_x_discrete(labels = c("dim_celek" = "Total", "dim_kratkodobapamet" = "Immediate memory", 
-    "dim_vizuoprostor" = "Visuospatial abilities", "dim_rec" = "Speech", "dim_pozornost" = "Attention",
-    "dim_dlouhodobapamet" = "Long term memory")) +
-    scale_fill_discrete(labels = c("baseline", "TP" = "Standard treatment",
-                                   "VR" = "VEs program")) +
+    scale_x_discrete(labels = c("iq_celek" = "Total", "iq_kratkodobapamet" = "Immediate memory", 
+      "iq_vizuoprostorschopnosti" = "Visuospatial/constructional", "iq_rec" = "Language", 
+      "iq_pozornost" = "Attention", "iq_dlouhodobapamet" = "Delayed memory")) +
+    scale_fill_manual(labels = c("baseline", "TP" = "Standard treatment",
+                                   "VR" = "VEs program"),
+                        values = CDZ_COLORS) +
     theme_apa() +
@@
           legend.position = c(0.5,1), legend.direction = "horizontal") +
-    labs(x = "", y = "Standardized score",
-         title = "Standardized scores of RBANS cognitive domains",
+    labs(x = "", y = "RBANS IQ score",
+         title = "IQ scores of RBANS cognitive domains",
          fill = "")
+
+ggsave("figures/fig2-rbans-iq.png",  width = 8, height = 6)
+
+df_rbans_long %>%
+  filter(subtest == "dim_rec") %>%
+  ggplot(aes(score, fill = factor(session))) + 
+  geom_histogram() + 
+  facet_wrap(~trenink)
 ```
@@
   filter(grepl("iq_", subtest)) %>%
-  mutate(session = paste0("session ", session - 1)) %>%
+  mutate(session = paste0("session ", session - 1),
+         fac_subtest = factor(subtest, levels = c("iq_celek", "iq_kratkodobapamet",
+                                                  "iq_dlouhodobapamet", "iq_rec",
+                                                  "iq_pozornost", "iq_vizuoprostorschopnosti"))) %>%
   ggplot(aes(subtest, score, fill = trenink)) +
-    geom_boxplot()
+    scale_x_discrete(labels = c("iq_celek" = "Total", "iq_kratkodobapamet" = "Immediate memory", 
+    "iq_vizuoprostorschopnosti" = "Visuospatial/constructional", "iq_rec" = "Language", 
+    "iq_pozornost" = "Attention", "iq_dlouhodobapamet" = "Delayed memory")) +
+    geom_boxplot() + 
+    theme_apa() +
+    scale_fill_manual(labels = c("baseline", "TP" = "Standard treatment",
+                                   "VR" = "VEs program"),
+                        values = CDZ_COLORS) +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1),
+          legend.position = c(0.5,1), legend.direction = "horizontal") +
+      labs(x = "", y = "RBANS IQ score",
+         title = "IQ scores of RBANS cognitive domains after each intervention",
+         fill = "")
+
+ggsave("figures/fig3-rbans-iq.png",  width = 8, height = 6)
 ```
+
+## Tesuceni
+
+Looking at the RBANS improvement as a function of a learning baseline bring significant results UNTIL we consider that the RBANS dimensions are not independent.
+In other works, person doing well on one often does well in others.
+We get significant effects of baseline tests in other tests as well (e.g.
+good baseline performance in orientace primky predicts good performance in ) When we control for the rbans dimension scores by their overall score in the session, the effect of the learning disappears.
+
+```{r}
+temp_mixed_func <- function(varname){
+  out <- df_temp %>%
+    filter(subtest == varname, session > 1) %>%
+    lmer(score ~ total_score + learning_baseline + factor(session) + (1|rbansid), data = .)
+  return(out)
+}
+
+df_temp2 <- baseline_rbans(df_rbans) %>%
+  left_join(select(df_rbans, rbansid, learning = testuceni), by = "rbansid")
+
+summary(lmer(dim_celek ~ learning + factor(session) + (1|rbansid), data = df_temp2))
+
+df_temp <- df_rbans_long %>%
+  arrange(rbansid, session) %>%
+  group_by(rbansid) %>%
+  mutate(learning_baseline = score[subtest == "testuceni"][1]) %>%
+  group_by(session, .add = TRUE) %>%
+  mutate(total_score = score[subtest == "dim_celek"][1]) %>%
+  ungroup()
+
+summary(temp_mixed_func("dim_kratkodobapamet"))
+summary(temp_mixed_func("dim_dlouhodobapamet"))
+summary(temp_mixed_func("dim_pozornost"))
+summary(temp_mixed_func("dim_rec"))
+summary(temp_mixed_func("dim_vizuoprostor"))
+
+dims <- c("dim_kratkodobapamet", "dim_dlouhodobapamet",
+          "dim_pozornost", "dim_rec", "dim_vizuoprostor")
+
+res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), 3)})
+knitr::kable(as.data.frame(res),
+             caption = "Testuceni in baseline as a predictor of rbans improvement controlled by rbans version (session) and total score")
+```

### 2021-03-23 reports/participant.Rmd
updates participant report

@@
 ---
-author: "Lukáš 'hejtmy' Hejtmánek"
-date: "`r Sys.Date()`"
+author: "Lukáš 'hejtmy' Hejtmánek (hejtmy@gmail.com)"
+date: "`r strftime(Sys.Date(), format = '%e. %m. %Y')`"
 output: html_document
@@
 library(tidyverse)
+library(helprs)
 source("../functions/cdz-loading-pilot.R")
@@
 source("../functions/cdz-getters.R")
-par <- list(data_dir = "E:/Google Drive/NUDZ/Projects/CDZ Karvina/VR-tasks/logy/2-pilot_VR-pen-paper/",
-               participant = "bohdan")
+par <- params
 df_sessions <- read.table("../sessions.csv", header = TRUE, sep = ";")
@@
 
-colors <- c("#63873a", "#f3f7e9", "#25aae1", "#81c6e2")
+CDZ_COLORS <- c("#63873a", "#f3f7e9", "#25aae1", "#81c6e2")
 ```
@@
             correct = mean(correct_ratio)) %>%
+  ungroup() %>%
+  mutate(date.posix = as.Date(date.posix)) %>%
   ggplot(aes(date.posix, max)) +
+    scale_x_date(date_labels = "%e.%B") +
     geom_line(aes(y = correct, color= "Úspěšnost"), size = 2) +
@@
     theme_bw() +
-    labs(title = "Maximální dosažená úroveň", x = "", y = "Úroveň") +
+    labs(title = "Maximální dosažená úroveň a úspěšnost", 
+         x = "", y = "Úroveň", colour = "") +
     theme(legend.position = "bottom")
@@
 
-XXX - problematické předměty
+```{r, results = 'asis'}
+generate_trial_graph <- function(exp, i){
+  trial <- get_trial_position(exp, i)
+  cat('<div class="col-md-4 col-sm-12">')
+    print(plot_supermarket_path(trial, background = TRUE, 
+          color = CDZ_COLORS[3], size = 2))
+  cat('</div>')
+}
+
+for(i in 1:length(exps)){
+  exp <- exps[[i]]
+  cat(as.character(htmltools::h3("Sezení ", i)))
+  i_trials <- get_finished_trials_indices.supermarket(exp)
+  for(i_trial in i_trials){
+    generate_trial_graph(exp, i_trial)
+  }
+  cat(as.character(htmltools::div(class="row", out)))
+}
+```

### 2021-03-23 reports/manuscript.Rmd
Udpates results knitrs

@@
 
-We have observed that patients suffering from schizophrenia had significantly worse baseline RBANS performance than patietns with affective disorders (see table XXX).
-This was one of the reasons we opted for the linear mixed modelling in our subsequent analyses as they should be able to control for the effect of diagnosis.
+We have observed that patients suffering from schizophrenia had significantly worse baseline RBANS performance than patients with MDD (see table XXX).
+This was one of the reasons we opted for the linear mixed modeling in our subsequent analyses as they should be able to control for the effect of diagnosis.
 
@@
 
-lmer_time_session_trial <- lmer(results_time ~ session + n_items + (1|participant), data = df_results_remediation)
-lmer_trajectory_session_trial <- lmer(results_trajectory ~ session + n_items + (1|participant), data = df_results_remediation)
-lmer_correct_session_6_9 <- lmer(correct_ratio ~ session + n_items + (1|participant), data = filter(df_results_remediation, n_items >= 6))
-
-lmer_ratio_session <- df_results_remediation %>%
-  lmer(correct_ratio ~ session + n_items + (1|rbansid), data = .)
-summary(lmer_ratio_session)
+lmer_time_session_trial <- lmer(results_time ~ session + n_items + (1|participant), 
+                                data = df_results_remediation)
+lmer_trajectory_session_trial <- lmer(results_trajectory ~ session + n_items + (1|participant), 
+                                      data = df_results_remediation)
+lmer_correct_session_6_9 <- lmer(correct_ratio ~ session + n_items + (1|participant), 
+                                 data = filter(df_results_remediation, n_items >= 6))
 ```
@@
           legend.position = c(0.5,1), legend.direction = "horizontal") +
-    labs(x = "", y = "RBANS IQ score",
-         title = "IQ scores of RBANS cognitive domains",
+    labs(x = "", y = "RBANS index score",
+         title = "Index scores of RBANS cognitive domains",
          fill = "")
@@
              Coefficients are for VR in contrast to TP (negative = VR does worse)")
-
 ```
@@
 
-```{r session model explanation,eval = FALSE}
+```{r session model explanation, eval = FALSE}
 temp_mixed_func <- function(varname){
@@
 knitr::kable(as.data.frame(res),
-             caption = "Trenink as a predictor of RBANS performance. Coefficients are for VR in contrast to TP (negative = VR does worse)")
+             caption = "Trenink as a predictor of RBANS performance.
+             Coefficients are for VR in contrast to TP (negative = VR does worse)")
 
@@
     geom_jitter(position = position_dodge(width = 0.5)) +
-    scale_fill_discrete(labels = c("baseline", "TP" = "Standard treatment", "VR" = "VEs program")) +
+    scale_fill_discrete(labels = c("baseline", "TP" = "Standard treatment",
+                                   "VR" = "VEs program")) +
     geom_hline(yintercept = 0.07) +
@@
 
+## Supplementary
+
+```{r diagnosis model, eval = TRUE}
+temp_mixed_func <- function(varname){
+  out <- df_rbans_long %>%
+    filter(subtest == varname, session > 1) %>%
+    lmer(z_score ~ trenink + diagnosis + factor(session) + (1|rbansid), data = .)
+  return(out)
+}
+
+lmer_celek <- temp_mixed_func("dim_celek")
+lmer_kratkodobapamet <- temp_mixed_func("dim_kratkodobapamet")
+lmer_dlouhodobapamet <- temp_mixed_func("dim_dlouhodobapamet")
+lmer_pozornost <- temp_mixed_func("dim_pozornost")
+lmer_rec <- temp_mixed_func("dim_rec")
+lmer_vizuoprostor <- temp_mixed_func("dim_vizuoprostor")
+
+dims <- c("dim_celek", "dim_kratkodobapamet", "dim_dlouhodobapamet",
+          "dim_pozornost", "dim_rec", "dim_vizuoprostor")
+res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), 3)})
+knitr::kable(as.data.frame(res),
+             caption = "Diagnosis as a predictor of RBANS performance. 
+             Coefficients are for schizophrenia in contrast to MDD (negative = schizophrenia does worse)")
+```
 ```{r}
@@
           legend.position = c(0.5,1), legend.direction = "horizontal") +
-      labs(x = "", y = "RBANS IQ score",
-         title = "IQ scores of RBANS cognitive domains after each intervention",
+      labs(x = "", y = "RBANS index score",
+         title = "Index scores of RBANS cognitive domains after each intervention",
          fill = "")
@@
 
-```{r}
+```{r effect of testuceni, eval=FALSE}
 temp_mixed_func <- function(varname){

### 2021-03-23 reports/knitting-participant.R
Updates participatn knitting pipeline

@@ -1,10 +1,15 @@
 library(withr)
 library(helprs)
-UNITY_DIR =  "E:/Google Drive/NUDZ/Projects/CDZ Karvina/VR-tasks/logy/2-pilot_VR-pen-paper/"
-parameters = list(data_dir = UNITY_DIR, participant = "bohdan")
+UNITY_DIR <- "E:/Google Drive/NUDZ/Projects/CDZ Karvina/VR-tasks/logy/2-pilot_VR-pen-paper/"
+participants <- list.dirs(file.path(UNITY_DIR, "supermarket"), recursive = FALSE, full.names = FALSE)
+
+#19 is zaloha
+for(n in participants[20:21]){
+parameters <- list(data_dir = UNITY_DIR, participant = n)
 with_locale(new = c('LC_CTYPE' = helprs::get_czech_platform_locale(),
                     'LC_TIME' = 'Czech'),
             rmarkdown::render("reports/participant.Rmd",
                               params = parameters,
                               output_dir = "reports/participants/",
                               output_file = parameters$participant))
+}

### 2021-07-24 reports/manuscript.Rmd
Updates manuscript with first review

@@
 
-```{r}
+```{r demographics tables}
 df_demographics_good %>%
@@
 
-```{r}
+```{r schizophrenia vs MDD demographics}
 df_demographics_good %>%
@@
   knitr::kable(digits = 3)
-
-df_rbans %>%
-  group_by()
-
 ```
@@
 ```{r}
+
 df_results_remediation %>%
@@
 ggsave("figures/fig1-session-difficulty.png",  width = 8, height = 6)
+
+df_results_remediation %>%
+  select(rbansid, session, max_difficulty) %>%
+  distinct() %>%
+  ggplot(aes(session, max_difficulty)) + 
+    geom_jitter(height = 0, width = 0.15) +
+    geom_smooth(method = "lm", fill = "grey80", color = "grey20") +
+    scale_x_continuous(breaks = seq(2,12,1)) + 
+    theme_apa() +
+    labs(y = "Maximum difficulty achieved", x = "Session")
+ggsave("figures/fig1-session-difficulty-bw.png",  width = 8, height = 6)
+
 ```
@@
 ```{r}
-df_rbans_long %>%
+fig2_rbans_iq <- df_rbans_long %>%
   filter(grepl("iq_", subtest)) %>%
@@
       "iq_pozornost" = "Attention", "iq_dlouhodobapamet" = "Delayed memory")) +
-    scale_fill_manual(labels = c("baseline", "TP" = "Standard treatment",
-                                   "VR" = "VEs program"),
-                        values = CDZ_COLORS) +
+
     theme_apa() +
@@
 
+fig2_rbans_iq + 
+  scale_fill_manual(labels = c("baseline", "TP" = "Standard treatment",
+                               "VR" = "VEs program"),
+                        values = CDZ_COLORS)
+
 ggsave("figures/fig2-rbans-iq.png",  width = 8, height = 6)
+
+fig2_rbans_iq + 
+  scale_fill_manual(labels = c("baseline", "TP" = "Standard treatment",
+                               "VR" = "VEs program"),
+                        values = colorRampPalette(c("white","grey40","grey80"))(3))
+
+ggsave("figures/fig2-rbans-iq-bw.png", width = 8, height = 6)
 
@@
 lmer_pozornost <- temp_mixed_func("dim_pozornost")
-lmer_rec <- temp_mixed_func("dim_rec")
+lmer_rec <- summary(temp_mixed_func("dim_rec"))
 lmer_vizuoprostor <- temp_mixed_func("dim_vizuoprostor")
@@
 ```
+
 ```{r}
-df_rbans_long %>%
+fig3_rbans_iq <- df_rbans_long %>%
   filter(grepl("iq_", subtest)) %>%
@@
     theme_apa() +
-    scale_fill_manual(labels = c("baseline", "TP" = "Standard treatment",
-                                   "VR" = "VEs program"),
-                        values = CDZ_COLORS) +
+
     theme(axis.text.x = element_text(angle = 45, hjust = 1),
@@
 
+fig3_rbans_iq + scale_fill_manual(labels = c("baseline", "TP" = "Standard treatment",
+                                            "VR" = "VEs program"), values = CDZ_COLORS)
 ggsave("figures/fig3-rbans-iq.png", width = 8, height = 6)
+
+fig3_rbans_iq + scale_fill_manual(labels = c("baseline", "TP" = "Standard treatment",
+                                            "VR" = "VEs program"),
+                                  values = colorRampPalette(c("white","grey40","grey80"))(3))
+ggsave("figures/fig3-rbans-iq-bw.png",width = 8, height = 6)
 ```
@@
 ```
+
+## Review 1.
+The reviewer asked for separation of Schizophrenia and MDD patients, given their different cognitive decline/performance
+
+```{r diagnosis as a predictor sessions 2-3}
+temp_mixed_func <- function(varname){
+  out <- df_rbans_long %>%
+    filter(subtest == varname, session > 1) %>%
+    lmer(z_score ~ diagnosis  + factor(session) + (1|rbansid), data = .)
+  return(out)
+}
+
+lmer_celek <- temp_mixed_func("dim_celek")
+lmer_kratkodobapamet <- temp_mixed_func("dim_kratkodobapamet")
+lmer_dlouhodobapamet <- temp_mixed_func("dim_dlouhodobapamet")
+lmer_pozornost <- temp_mixed_func("dim_pozornost")
+lmer_rec <- summary(temp_mixed_func("dim_rec"))
+lmer_vizuoprostor <- temp_mixed_func("dim_vizuoprostor")
+
+dims <- c("dim_celek", "dim_kratkodobapamet", "dim_dlouhodobapamet",
+          "dim_pozornost", "dim_rec", "dim_vizuoprostor")
+res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), 3)})
+knitr::kable(as.data.frame(res),
+             caption = "Diagnosis as a predictor of RBANS performance in sessions 2 and 3. 
+             Coefficients are for schizophrenia in contrast to MDD (negative = schizophrenia does worse)")
+```
+
+```{r diagnosis as a predictor all sessions}
+temp_mixed_func <- function(varname){
+  out <- df_rbans_long %>%
+    filter(subtest == varname) %>%
+    lmer(z_score ~ diagnosis + session + (1|rbansid), data = .)
+  return(out)
+}
+
+lmer_celek <- temp_mixed_func("dim_celek")
+lmer_kratkodobapamet <- temp_mixed_func("dim_kratkodobapamet")
+lmer_dlouhodobapamet <- temp_mixed_func("dim_dlouhodobapamet")
+lmer_pozornost <- temp_mixed_func("dim_pozornost")
+lmer_rec <- summary(temp_mixed_func("dim_rec"))
+lmer_vizuoprostor <- temp_mixed_func("dim_vizuoprostor")
+
+dims <- c("dim_celek", "dim_kratkodobapamet", "dim_dlouhodobapamet",
+          "dim_pozornost", "dim_rec", "dim_vizuoprostor")
+res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), "diagnosisschizophrenia")})
+knitr::kable(as.data.frame(res),
+             caption = "Diagnosis as a predictor of RBANS performance while controlling for the effect of participant and session.
+             Coefficients are for schizophrenia in contrast to MDD (negative = schizophrenia does worse)")
+
+res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), "session")})
+knitr::kable(as.data.frame(res),
+             caption = "Session as a predictor of RBANS performance while controlling for the effect of participant and diagnosis.
+             negative = patients do worse and worse")
+```
+
+```{r}
+df_rbans_long %>%
+  filter(subtest == "dim_celek") %>%
+  ggplot(aes(session, z_score)) +
+  geom_point(position=position_jitter(width=0.2)) +
+  geom_smooth(method="lm") +
+  scale_x_continuous(breaks = 1:3) +
+  facet_wrap(~diagnosis)
+```
+
+```{r only MDD patient}
+temp_mixed_func <- function(varname, diagnosis){
+  out <- df_rbans_long %>%
+    filter(subtest == varname, session > 1, diagnosis == "affective disorders") %>%
+    lmer(z_score ~ factor(session) + (1|rbansid), data = .)
+  return(out)
+}
+
+lmer_celek <- temp_mixed_func("dim_celek")
+lmer_kratkodobapamet <- temp_mixed_func("dim_kratkodobapamet")
+lmer_dlouhodobapamet <- temp_mixed_func("dim_dlouhodobapamet")
+lmer_pozornost <- temp_mixed_func("dim_pozornost")
+lmer_rec <- summary(temp_mixed_func("dim_rec"))
+lmer_vizuoprostor <- temp_mixed_func("dim_vizuoprostor")
+
+dims <- c("dim_celek", "dim_kratkodobapamet", "dim_dlouhodobapamet",
+          "dim_pozornost", "dim_rec", "dim_vizuoprostor")
+res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), "factor(session)3")})
+knitr::kable(as.data.frame(res),
+             caption = "Session as a predictor of RBANS performance for patients in MDD. 
+             Coefficients are for third session in contrast to the second (negative = patients do worse in 3rd session)")
+```
+
+```{r only SZ patient}
+temp_mixed_func <- function(varname){
+  out <- df_rbans_long %>%
+    filter(subtest == varname, session > 1, diagnosis == "schizophrenia") %>%
+    lmer(z_score ~ factor(session) + (1|rbansid), data = .)
+  return(out)
+}
+
+lmer_celek <- temp_mixed_func("dim_celek")
+lmer_kratkodobapamet <- temp_mixed_func("dim_kratkodobapamet")
+lmer_dlouhodobapamet <- temp_mixed_func("dim_dlouhodobapamet")
+lmer_pozornost <- temp_mixed_func("dim_pozornost")
+lmer_rec <- summary(temp_mixed_func("dim_rec"))
+lmer_vizuoprostor <- temp_mixed_func("dim_vizuoprostor")
+
+dims <- c("dim_celek", "dim_kratkodobapamet", "dim_dlouhodobapamet",
+          "dim_pozornost", "dim_rec", "dim_vizuoprostor")
+res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), "factor(session)3")})
+knitr::kable(as.data.frame(res),
+             caption = "Session as a predictor of RBANS performance for patients with schizophrenia. 
+             Coefficients are for third session in contrast to the second (negative = patients do worse in 3rd session)")
+```
+
+```{r only SZ patient linear session}
+temp_mixed_func <- function(varname){
+  out <- df_rbans_long %>%
+    filter(subtest == varname, diagnosis == "schizophrenia") %>%
+    lmer(z_score ~ session + (1|rbansid), data = .)
+  return(out)
+}
+
+lmer_celek <- temp_mixed_func("dim_celek")
+lmer_kratkodobapamet <- temp_mixed_func("dim_kratkodobapamet")
+lmer_dlouhodobapamet <- temp_mixed_func("dim_dlouhodobapamet")
+lmer_pozornost <- temp_mixed_func("dim_pozornost")
+lmer_rec <- summary(temp_mixed_func("dim_rec"))
+lmer_vizuoprostor <- temp_mixed_func("dim_vizuoprostor")
+
+dims <- c("dim_celek", "dim_kratkodobapamet", "dim_dlouhodobapamet",
+          "dim_pozornost", "dim_rec", "dim_vizuoprostor")
+res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), 2)})
+knitr::kable(as.data.frame(res),
+             caption = "Session as a predictor of RBANS performance for patients with schizophrenia. 
+             Coefficients are for session as a linear predictor (1,2,3) negative = patients do worse and worse")
+```
+
+```{r only MDD patient linear session}
+temp_mixed_func <- function(varname){
+  out <- df_rbans_long %>%
+    filter(subtest == varname, diagnosis == "affective disorders") %>%
+    lmer(z_score ~ session + (1|rbansid), data = .)
+  return(out)
+}
+
+lmer_celek <- temp_mixed_func("dim_celek")
+lmer_kratkodobapamet <- temp_mixed_func("dim_kratkodobapamet")
+lmer_dlouhodobapamet <- temp_mixed_func("dim_dlouhodobapamet")
+lmer_pozornost <- temp_mixed_func("dim_pozornost")
+lmer_rec <- summary(temp_mixed_func("dim_rec"))
+lmer_vizuoprostor <- temp_mixed_func("dim_vizuoprostor")
+
+dims <- c("dim_celek", "dim_kratkodobapamet", "dim_dlouhodobapamet",
+          "dim_pozornost", "dim_rec", "dim_vizuoprostor")
+res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), 2)})
+knitr::kable(as.data.frame(res),
+             caption = "Session as a predictor of RBANS performance for patients with affective disorders. 
+             Coefficients are for session as a linear predictor (1,2,3) negative = patients do worse and worse")
+```
+
+```{r temp}
+df_rbans_long %>%
+  filter(diagnosis =="affective disorders", subtest=="dim_celek")
+
+df_rbans %>%
+  filter(diagnosis=="affective disorders", !is.na(testpameti)) %>%
+  count(rbansid)
+```

### 2021-07-24 reports/rbans-output.Rmd
Updates manuscript with first review

@@
 
+good_participants <- df_rbans %>%
+  group_by(rbansid) %>%
+  filter(!is.na(testpameti)) %>%
+  summarise(n = n()) %>%
+  filter(n >= 2) %>%
+  pull(rbansid)
+
+df_rbans <- df_rbans %>%
+  filter(rbansid %in% good_participants)
+
 df_rbans_long <- df_rbans %>%
     pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
-                 names_to = "subtest", values_to = "score")
+                 names_to = "subtest", values_to = "score") %>%
+  group_by(session, subtest) %>%
+  mutate(z_score = scale(score)[,1])
 
@@
   group_by(trenink, first_training, subtest) %>%
-  summarise(group_avg = mean(score, na.rm = TRUE)) %>%
+  summarise(group_avg = mean(score, na.rm = TRUE),
+            group_z_avg = mean(z_score, na.rm = TRUE),
+            .groups="drop") %>%
   right_join(df_rbans_long, by = c("trenink", "first_training", "subtest"))
 ```
+
 ```{r}
@@
 ```
+
+```{r}
+df_rbans_long %>%
+  filter(!grepl("(iq_|dim_)", subtest)) %>%
+  ggplot(aes(subtest, score, fill = factor(session))) + geom_boxplot() +
+   theme(axis.text.x = element_text(angle = 45, hjust = 1),
+          legend.position = c(0.5,1), legend.direction = "horizontal") +
+  facet_wrap(~trenink)
+```
+
+```{r}
+df_rbans_long %>%
+  filter(grepl("(iq_)", subtest)) %>%
+  ggplot(aes(subtest, score, fill = factor(session))) + geom_boxplot() +
+   theme(axis.text.x = element_text(angle = 45, hjust = 1),
+          legend.position = c(0.5,1), legend.direction = "horizontal")
+```

### 2021-07-24 functions/cdz-getters.R

@@ -16,7 +16,7 @@ get_sheet_demographics <- function(preprocess = TRUE, overwrite = FALSE){
   GS_RUN2_DEMOGRAPHICS_RBANS <- "1qMdiLYY7EIbNvoRsE5knjBB24zXT7hgJNUCmwMX7IwY"
   df_demographics <- googlesheets4::range_read(GS_RUN2_DEMOGRAPHICS_RBANS, 
                                              sheet = "demografie", 
-                                             col_types = "ccccccciiiccci")
+                                             col_types = "ccccccciiicccicc")
   if(!preprocess) return(df_demographics)
   colnames(df_demographics) <- c("name", "note", "first_training", "rbans_date",
                                  "rbansid", "retirement", "gender", "age",

### 2021-07-25 reports/manuscript.Rmd
updates manuscript review section

@@
     filter(subtest == varname) %>%
-    lmer(z_score ~ diagnosis + session + (1|rbansid), data = .)
+    lmer(score ~ diagnosis*session + (1|rbansid), data = .)
   return(out)
@@
           "dim_pozornost", "dim_rec", "dim_vizuoprostor")
+res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), "diagnosisschizophrenia:session")})
+knitr::kable(as.data.frame(res),
+             caption = "Interaction between diagnosis and session as a predictor of RBANS performance while controlling for the effect of participant and session.
+Coefficients are for schizophrenia in contrast to MDD (negative = schizophrenia does worse)")
+
 res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), "diagnosisschizophrenia")})
